---
title: "Analysis"
author: "Tianqi Ouyang"
date: "2026-03-31"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-analysis
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load final_master from data management output
final_master <- readRDS("final_master.rds")
```

# 2 Derived Variables

```{r}
#| label: derived-vars
final_master <- final_master %>%
  mutate(
    hosp_90 = case_when(
      hosp_status_90d == 1 ~ 1,
      hosp_status_90d == 2 ~ 0,
      TRUE ~ NA_real_
    ),
    platinum_related_hosp = ifelse(side_effect == 1, 1, 0),
    dd_percentile = ntile(dose_discrepancy, 100),
    dd_decile     = ntile(dose_discrepancy, 10)
  )
```

# 3 Table 1: Baseline Characteristics

```{r}
#| label: table1-baseline
table_one <- final_master %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    carbo_AUC, carbo_AUC_cat,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    carbo_dose_redcap, carbo_dose_cre_cys, dose_discrepancy, dose_diff_pct
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
table_one
```

## 3.1 Table 1 by Carboplatin AUC Category

```{r}
#| label: table1-carbo-auc-cat
table1_vars <- c(
  "age", "age_cat", "sex", "race", "ethnicity", "tumor_stage", "cancer_type_cat_7",
  "carbo_AUC",
  "ici", "Bevacizumab", "Paclitaxel", "Pemetrexed", "Doxorubicin", "Etoposide",
  "Gemcitabine", "Pertuzumab", "Trastuzumab", "Docetaxel", "Administered_alone",
  "hiv_rpdr", "thyroid", "smoking", "steroids",
  "cci", "ecog_score", "bmi", "bmi_cat",
  "pre_HGB_45days", "pre_PLT_45days", "pre_ALB_45days",
  "baseline_cys_c", "baseline_cre",
  "baseline_cre_egfr", "baseline_cys_c_egfr",
  "ckd_epi_gfr_cre_cys", "ckd_epi_gfr_cre_cys_unindex",
  "carbo_dose_redcap", "carbo_dose_cre_cys", "dose_discrepancy", "dose_diff_pct"
)

final_master %>%
  dplyr::select(all_of(table1_vars), carbo_AUC_cat) %>%
  tbl_summary(
    by = carbo_AUC_cat,
    statistic = list(age ~ "{mean} ({sd})")
  ) %>%
  add_overall() %>%
  add_p(test.args = list(all_categorical() ~ list(simulate.p.value = TRUE)))
```

## 3.2 Table 1 by Dose Discrepancy > 25 mg

```{r}
#| label: table1-dd-gt25
final_master %>%
  dplyr::select(all_of(table1_vars), dd_gt25) %>%
  tbl_summary(
    by = dd_gt25,
    statistic = list(age ~ "{mean} ({sd})")
  ) %>%
  add_overall() %>%
  add_p(test.args = list(all_categorical() ~ list(simulate.p.value = TRUE)))
```

## 3.3 Table 1 by Dose Discrepancy > 50 mg

```{r}
#| label: table1-dd-gt50
final_master %>%
  dplyr::select(all_of(table1_vars), dd_gt50) %>%
  tbl_summary(
    by = dd_gt50,
    statistic = list(age ~ "{mean} ({sd})")
  ) %>%
  add_overall() %>%
  add_p(test.args = list(all_categorical() ~ list(simulate.p.value = TRUE)))
```

## 3.4 Incidence Outcomes

```{r}
#| label: table1-incidence
outcome_vars <- c("Anemia_g2_90days", "Anemia_g3_90days",
                   "Throm_g2_90days", "Throm_g3_90days",
                   "AKI_g2_90days", "AKI_g3_90days",
                   "grade_2_aes", "grade_3_aes",
                   "hosp_90", "platinum_related_hosp", "death_90")

# Overall
table_one_incidence <- final_master %>%
  select(all_of(outcome_vars)) %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 1
    )
  )
table_one_incidence
```

## 3.5 Incidence Outcomes by Carboplatin AUC Category

```{r}
#| label: table1-incidence-carbo-auc
final_master %>%
  select(all_of(outcome_vars), carbo_AUC_cat) %>%
  tbl_summary(
    by = carbo_AUC_cat,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 1
    )
  ) %>%
  add_overall() %>%
  add_p(test.args = list(all_categorical() ~ list(simulate.p.value = TRUE)))
```

# 4 Dose Distribution

## 4.1 Actual vs Predicted Dose (Overlaid)

```{r}
#| label: plot-dose-overlay
dose_long <- final_master %>%
  select(record_id, carbo_dose_redcap, carbo_dose_cre_cys) %>%
  pivot_longer(
    cols = c(carbo_dose_redcap, carbo_dose_cre_cys),
    names_to = "dose_type", values_to = "dose_mg"
  ) %>%
  filter(!is.na(dose_mg)) %>%
  mutate(dose_type = case_match(dose_type,
    "carbo_dose_redcap"  ~ "Actual (REDCap)",
    "carbo_dose_cre_cys" ~ "Predicted (CKD-EPI Cr-Cys)"
  ))

ggplot(dose_long, aes(x = dose_mg, fill = dose_type)) +
  geom_histogram(alpha = 0.5, bins = 40, position = "identity", color = "black") +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution",
       x = "Dose (mg)", y = "Number of Patients", fill = "Dose Type") +
  theme_minimal(base_size = 14)
```

## 4.2 Actual vs Predicted Dose (Side by Side)

```{r}
#| label: plot-dose-facet
ggplot(dose_long, aes(x = dose_mg, fill = dose_type)) +
  geom_histogram(color = "black", alpha = 0.7, bins = 40) +
  facet_wrap(~ dose_type) +
  geom_vline(
    data = dose_long %>% group_by(dose_type) %>%
      summarise(grp_mean = mean(dose_mg, na.rm = TRUE)),
    aes(xintercept = grp_mean), color = "red", linetype = "dashed", linewidth = 0.8
  ) +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution",
       x = "Dose (mg)", y = "Number of Patients") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
```

```{r}
#| label: decile-rates
final_master <- final_master %>%
  group_by(dd_decile) %>%
  mutate(
    anemia_2_rate_decile              = mean(Anemia_g2_90days, na.rm = TRUE),
    anemia_3_rate_decile              = mean(Anemia_g3_90days, na.rm = TRUE),
    throm_2_rate_decile               = mean(Throm_g2_90days, na.rm = TRUE),
    throm_3_rate_decile               = mean(Throm_g3_90days, na.rm = TRUE),
    aki_2_rate_decile                 = mean(AKI_g2_90days, na.rm = TRUE),
    aki_3_rate_decile                 = mean(AKI_g3_90days, na.rm = TRUE),
    hos_rate_decile                   = mean(hosp_90, na.rm = TRUE),
    platinum_related_hos_rate_decile  = mean(platinum_related_hosp, na.rm = TRUE),
    death_rate_decile                 = mean(death_90, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(dd_decile = as.numeric(dd_decile))
```

# 5 LOESS Plots: AE Rates by Dose Discrepancy Percentile

```{r}
#| label: compute-vline-medians
# Median dose discrepancy at 60th and 70th percentile (for vertical line labels)
median_dd_p60 <- median(
  final_master$dose_discrepancy[final_master$dd_percentile == 60], na.rm = TRUE)
median_dd_p70 <- median(
  final_master$dose_discrepancy[final_master$dd_percentile == 70], na.rm = TRUE)
```

```{r}
#| label: fn-loess-plot
loess_plot <- function(data, x, y, x_point, y_point, title, xlab, ylab,
                       vlines = NULL) {
  p <- ggplot(data, aes(x = {{x}}, y = {{y}})) +
    geom_point(aes(x = {{x_point}}, y = {{y_point}}),
               size = 4, color = "black", shape = 19) +
    geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue", linewidth = 1.5) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(title = title, x = xlab, y = ylab) +
    theme_minimal(base_size = 12) +
    theme(
      axis.title.x  = element_text(size = 11),
      axis.title.y  = element_text(size = 11),
      axis.text.x   = element_text(size = 10),
      axis.text.y   = element_text(size = 10),
      plot.title     = element_text(size = 13, face = "bold")
    )
  if (!is.null(vlines)) {
    p <- p +
      geom_vline(data = vlines, aes(xintercept = x),
                 linetype = "dashed", color = "red", linewidth = 0.7) +
      geom_text(data = vlines, aes(x = x, y = Inf, label = label),
                vjust = 1.5, hjust = -0.1, size = 3.2, color = "red")
  }
  p
}

loess_plot_raw <- function(data, x, y, title, xlab, ylab, vlines = NULL) {
  p <- ggplot(data, aes(x = {{x}}, y = {{y}})) +
    geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue", linewidth = 1.5) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(title = title, x = xlab, y = ylab) +
    theme_minimal(base_size = 12) +
    theme(
      axis.title.x  = element_text(size = 11),
      axis.title.y  = element_text(size = 11),
      axis.text.x   = element_text(size = 10),
      axis.text.y   = element_text(size = 10),
      plot.title     = element_text(size = 13, face = "bold")
    )
  if (!is.null(vlines)) {
    p <- p +
      geom_vline(data = vlines, aes(xintercept = x),
                 linetype = "dashed", color = "red", linewidth = 0.7) +
      geom_text(data = vlines, aes(x = x, y = Inf, label = label),
                vjust = 1.5, hjust = -0.1, size = 3.2, color = "red")
  }
  p
}
```

```{r}
#| label: vline-data
# Vertical reference lines for percentile LOESS plots
pct_vlines <- data.frame(
  x     = c(60, 70),
  label = c(paste0("median: ", round(median_dd_p60, 0), ""),
            paste0("median: ", round(median_dd_p70, 0), ""))
)
```

## 5.1 Grade 2 Anemia

```{r}
#| label: plot-anemia-2
loess_plot(
  data = final_master, x = dd_percentile, y = Anemia_g2_90days,
  x_point = dd_decile * 10, y_point = anemia_2_rate_decile,
  title = "Grade >= 2 Anemia",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Anemia",
  vlines = pct_vlines
)
```

## 5.2 Grade 3 Anemia

```{r}
#| label: plot-anemia-3
loess_plot(
  data = final_master, x = dd_percentile, y = Anemia_g3_90days,
  x_point = dd_decile * 10, y_point = anemia_3_rate_decile,
  title = "Grade >= 3 Anemia",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Anemia",
  vlines = pct_vlines
)
```

## 5.3 Grade 2 Thrombocytopenia

```{r}
#| label: plot-throm-2
loess_plot(
  data = final_master, x = dd_percentile, y = Throm_g2_90days,
  x_point = dd_decile * 10, y_point = throm_2_rate_decile,
  title = "Grade >= 2 Thrombocytopenia",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Thrombocytopenia",
  vlines = pct_vlines
)
```

## 5.4 Grade 3 Thrombocytopenia

```{r}
#| label: plot-throm-3
loess_plot(
  data = final_master, x = dd_percentile, y = Throm_g3_90days,
  x_point = dd_decile * 10, y_point = throm_3_rate_decile,
  title = "Grade >= 3 Thrombocytopenia",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Thrombocytopenia",
  vlines = pct_vlines
)
```

## 5.5 Grade 2 AKI

```{r}
#| label: plot-aki-2
loess_plot(
  data = final_master, x = dd_percentile, y = AKI_g2_90days,
  x_point = dd_decile * 10, y_point = aki_2_rate_decile,
  title = "Grade >= 2 Creatinine Increased",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Creatinine Increased",
  vlines = pct_vlines
)
```

## 5.6 Grade 3 AKI

```{r}
#| label: plot-aki-3
loess_plot(
  data = final_master, x = dd_percentile, y = AKI_g3_90days,
  x_point = dd_decile * 10, y_point = aki_3_rate_decile,
  title = "Grade >= 3 Creatinine Increased",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Creatinine Increased",
  vlines = pct_vlines
)
```

## 5.7 Overall Hospitalization

```{r}
#| label: plot-hosp
loess_plot(
  data = final_master, x = dd_percentile, y = hosp_90,
  x_point = dd_decile * 10, y_point = hos_rate_decile,
  title = "Overall Hospitalization",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Overall Hospitalization",
  vlines = pct_vlines
)
```

## 5.8 Platinum-Related Hospitalization

```{r}
#| label: plot-platinum-hosp
loess_plot(
  data = final_master, x = dd_percentile, y = platinum_related_hosp,
  x_point = dd_decile * 10, y_point = platinum_related_hos_rate_decile,
  title = "Hospitalization for Platinum-Associated AEs",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Hospitalization for Platinum-Associated AEs",
  vlines = pct_vlines
)
```

## 5.9 90-Day Death

```{r}
#| label: plot-death-pct
loess_plot(
  data = final_master, x = dd_percentile, y = death_90,
  x_point = dd_decile * 10, y_point = death_rate_decile,
  title = "90-Day Mortality",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "90-Day Mortality",
  vlines = pct_vlines
)
```

# 6 LOESS Plots: AE Rates by Actual Dose Discrepancy (mg)

```{r}
#| label: raw-vline-data
raw_vlines <- data.frame(
  x     = c(25, 50, 75),
  label = c("25 mg", "50 mg", "75 mg")
)
```

## 6.1 Grade 2 Anemia

```{r}
#| label: plot-anemia-2-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = Anemia_g2_90days,
  title = "Grade >= 2 Anemia",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Anemia",
  vlines = raw_vlines
)
```

## 6.2 Grade 3 Anemia

```{r}
#| label: plot-anemia-3-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = Anemia_g3_90days,
  title = "Grade >= 3 Anemia",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Anemia",
  vlines = raw_vlines
)
```

## 6.3 Grade 2 Thrombocytopenia

```{r}
#| label: plot-throm-2-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = Throm_g2_90days,
  title = "Grade >= 2 Thrombocytopenia",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Thrombocytopenia",
  vlines = raw_vlines
)
```

## 6.4 Grade 3 Thrombocytopenia

```{r}
#| label: plot-throm-3-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = Throm_g3_90days,
  title = "Grade >= 3 Thrombocytopenia",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Thrombocytopenia",
  vlines = raw_vlines
)
```

## 6.5 Grade 2 AKI

```{r}
#| label: plot-aki-2-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = AKI_g2_90days,
  title = "Grade >= 2 Creatinine Increased",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Creatinine Increased",
  vlines = raw_vlines
)
```

## 6.6 Grade 3 AKI

```{r}
#| label: plot-aki-3-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = AKI_g3_90days,
  title = "Grade >= 3 Creatinine Increased",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Creatinine Increased",
  vlines = raw_vlines
)
```

## 6.7 Overall Hospitalization

```{r}
#| label: plot-hosp-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = hosp_90,
  title = "Overall Hospitalization",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Overall Hospitalization",
  vlines = raw_vlines
)
```

## 6.8 Platinum-Related Hospitalization

```{r}
#| label: plot-platinum-hosp-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = platinum_related_hosp,
  title = "Hospitalization for Platinum-Associated AEs",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Hospitalization for Platinum-Associated AEs",
  vlines = raw_vlines
)
```

## 6.9 90-Day Death

```{r}
#| label: plot-death-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = death_90,
  title = "90-Day Mortality",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "90-Day Mortality",
  vlines = raw_vlines
)
```

# 7 Dose Discrepancy: Outlier Inspection

```{r}
#| label: plot-dose-diff-boxplot
# IQR-based outlier detection
dd_stats <- boxplot.stats(final_master$dose_discrepancy[!is.na(final_master$dose_discrepancy)])

cat("Dose Discrepancy Summary:\n")
cat("  Median:", median(final_master$dose_discrepancy, na.rm = TRUE), "mg\n")
cat("  IQR:   ", IQR(final_master$dose_discrepancy, na.rm = TRUE), "mg\n")
cat("  Lower fence:", dd_stats$stats[1], "mg\n")
cat("  Upper fence:", dd_stats$stats[5], "mg\n")
cat("  N outliers: ", length(dd_stats$out), "\n")

# Flag outlier patients
outlier_ids <- final_master %>%
  filter(dose_discrepancy %in% dd_stats$out) %>%
  select(record_id, EMPI, carbo_AUC, carbo_dose_redcap, carbo_dose_cre_cys,
         dose_discrepancy, dose_diff_pct,
         ckd_epi_gfr_cre_cys_unindex, ckd_epi_gfr_cre_cys_unindex_cap125)

cat("\nOutlier record_ids:\n")
print(outlier_ids %>% select(record_id, dose_discrepancy, dose_diff_pct, carbo_AUC,
                              carbo_dose_redcap, carbo_dose_cre_cys),
      n = Inf)
```

```{r}
#| label: plot-boxplot-dd
ggplot(final_master, aes(y = dose_discrepancy)) +
  geom_boxplot(fill = "#1F78B4", alpha = 0.5, outlier.color = "red", outlier.size = 2) +
  labs(title = "Dose Discrepancy: Boxplot with Outliers",
       y = "Dose Discrepancy (mg): Actual - Predicted",
       subtitle = "Red points = IQR outliers") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```

# 8 Cumulative Incidence Plots

## 8.1 Platinum-Related Hospitalization by dd_gt25

```{r}
#| label: cuminc-side-effect-dd25
fit_side_effect_dd25 <- cuminc(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt25,
  data = final_master
)

ggcuminc(fit_side_effect_dd25) +
  labs(
    title = "Platinum-Related Hospitalization by Dose Discrepancy > 25 mg",
    x = "Follow-up Time (Days)",
    y = "Cumulative Incidence"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_classic(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold", size = 16),
    axis.title    = element_text(size = 14),
    axis.text     = element_text(size = 12),
    legend.title  = element_blank(),
    legend.text   = element_text(size = 12)
  ) +
  scale_color_manual(values = c("red", "blue"))
```

## 8.2 Platinum-Related Hospitalization by dd_gt50

```{r}
#| label: cuminc-side-effect-dd50
fit_side_effect_dd50 <- cuminc(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt50,
  data = final_master
)

ggcuminc(fit_side_effect_dd50) +
  labs(
    title = "Platinum-Related Hospitalization by Dose Discrepancy > 50 mg",
    x = "Follow-up Time (Days)",
    y = "Cumulative Incidence"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_classic(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold", size = 16),
    axis.title    = element_text(size = 14),
    axis.text     = element_text(size = 12),
    legend.title  = element_blank(),
    legend.text   = element_text(size = 12)
  ) +
  scale_color_manual(values = c("red", "blue"))
```

## 8.3 Kaplan-Meier: 90-Day Death by dd_gt25

```{r}
#| label: km-death-dd25
km_death_dd25 <- survfit(
  Surv(time_to_death_90, death_90) ~ dd_gt25,
  data = final_master
)

ggsurvfit(km_death_dd25) +
  labs(
    title = "90-Day Mortality by Dose Discrepancy > 25 mg",
    x = "Follow-up Time (Days)",
    y = "Survival Probability"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_classic(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold", size = 16),
    axis.title    = element_text(size = 14),
    axis.text     = element_text(size = 12),
    legend.title  = element_blank(),
    legend.text   = element_text(size = 12)
  ) +
  scale_color_manual(values = c("red", "blue"))
```

## 8.4 Kaplan-Meier: 90-Day Death by dd_gt50

```{r}
#| label: km-death-dd50
km_death_dd50 <- survfit(
  Surv(time_to_death_90, death_90) ~ dd_gt50,
  data = final_master
)

ggsurvfit(km_death_dd50) +
  labs(
    title = "90-Day Mortality by Dose Discrepancy > 50 mg",
    x = "Follow-up Time (Days)",
    y = "Survival Probability"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_classic(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold", size = 16),
    axis.title    = element_text(size = 14),
    axis.text     = element_text(size = 12),
    legend.title  = element_blank(),
    legend.text   = element_text(size = 12)
  ) +
  scale_color_manual(values = c("red", "blue"))
```

# 9 LOESS Plots: Carboplatin AUC < 4 Cohort

```{r}
#| label: carbo-lt4-subset
# Subset to carboplatin patients with AUC < 4
fm_lt4 <- final_master %>%
  filter(carbo_AUC_cat == "<4")

# Recompute percentile and decile within this subset
fm_lt4 <- fm_lt4 %>%
  mutate(
    dd_percentile_lt4 = ntile(dose_discrepancy, 100),
    dd_decile_lt4     = ntile(dose_discrepancy, 10)
  ) %>%
  group_by(dd_decile_lt4) %>%
  mutate(
    anemia_2_rate_decile_lt4             = mean(Anemia_g2_90days, na.rm = TRUE),
    anemia_3_rate_decile_lt4             = mean(Anemia_g3_90days, na.rm = TRUE),
    throm_2_rate_decile_lt4              = mean(Throm_g2_90days, na.rm = TRUE),
    throm_3_rate_decile_lt4              = mean(Throm_g3_90days, na.rm = TRUE),
    aki_2_rate_decile_lt4                = mean(AKI_g2_90days, na.rm = TRUE),
    aki_3_rate_decile_lt4                = mean(AKI_g3_90days, na.rm = TRUE),
    hos_rate_decile_lt4                  = mean(hosp_90, na.rm = TRUE),
    platinum_related_hos_rate_decile_lt4 = mean(platinum_related_hosp, na.rm = TRUE),
    death_rate_decile_lt4                = mean(death_90, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(dd_decile_lt4 = as.numeric(dd_decile_lt4))
```

```{r}
#| label: carbo-lt4-vlines
# Median dose discrepancy at P60 and P70 within the AUC < 4 subset
median_dd_p60_lt4 <- median(
  fm_lt4$dose_discrepancy[fm_lt4$dd_percentile_lt4 == 60], na.rm = TRUE)
median_dd_p70_lt4 <- median(
  fm_lt4$dose_discrepancy[fm_lt4$dd_percentile_lt4 == 70], na.rm = TRUE)

pct_vlines_lt4 <- data.frame(
  x     = c(60, 70),
  label = c(paste0("median: ", round(median_dd_p60_lt4, 0), ""),
            paste0("median: ", round(median_dd_p70_lt4, 0), ""))
)
```

## 9.1 Grade 2 Anemia (AUC < 4)

```{r}
#| label: plot-anemia-2-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = Anemia_g2_90days,
  x_point = dd_decile_lt4 * 10, y_point = anemia_2_rate_decile_lt4,
  title = "Grade >= 2 Anemia (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Anemia",
  vlines = pct_vlines_lt4
)
```

## 9.2 Grade 3 Anemia (AUC < 4)

```{r}
#| label: plot-anemia-3-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = Anemia_g3_90days,
  x_point = dd_decile_lt4 * 10, y_point = anemia_3_rate_decile_lt4,
  title = "Grade >= 3 Anemia (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Anemia",
  vlines = pct_vlines_lt4
)
```

## 9.3 Grade 2 Thrombocytopenia (AUC < 4)

```{r}
#| label: plot-throm-2-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = Throm_g2_90days,
  x_point = dd_decile_lt4 * 10, y_point = throm_2_rate_decile_lt4,
  title = "Grade >= 2 Thrombocytopenia (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Thrombocytopenia",
  vlines = pct_vlines_lt4
)
```

## 9.4 Grade 3 Thrombocytopenia (AUC < 4)

```{r}
#| label: plot-throm-3-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = Throm_g3_90days,
  x_point = dd_decile_lt4 * 10, y_point = throm_3_rate_decile_lt4,
  title = "Grade >= 3 Thrombocytopenia (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Thrombocytopenia",
  vlines = pct_vlines_lt4
)
```

## 9.5 Grade 2 AKI (AUC < 4)

```{r}
#| label: plot-aki-2-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = AKI_g2_90days,
  x_point = dd_decile_lt4 * 10, y_point = aki_2_rate_decile_lt4,
  title = "Grade >= 2 Creatinine Increased (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Creatinine Increased",
  vlines = pct_vlines_lt4
)
```

## 9.6 Grade 3 AKI (AUC < 4)

```{r}
#| label: plot-aki-3-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = AKI_g3_90days,
  x_point = dd_decile_lt4 * 10, y_point = aki_3_rate_decile_lt4,
  title = "Grade >= 3 Creatinine Increased (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Creatinine Increased",
  vlines = pct_vlines_lt4
)
```

## 9.7 Overall Hospitalization (AUC < 4)

```{r}
#| label: plot-hosp-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = hosp_90,
  x_point = dd_decile_lt4 * 10, y_point = hos_rate_decile_lt4,
  title = "Overall Hospitalization (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Overall Hospitalization",
  vlines = pct_vlines_lt4
)
```

## 9.8 Platinum-Related Hospitalization (AUC < 4)

```{r}
#| label: plot-platinum-hosp-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = platinum_related_hosp,
  x_point = dd_decile_lt4 * 10, y_point = platinum_related_hos_rate_decile_lt4,
  title = "Hospitalization for Platinum-Associated AEs (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Hospitalization for Platinum-Associated AEs",
  vlines = pct_vlines_lt4
)
```

## 9.9 90-Day Death (AUC < 4)

```{r}
#| label: plot-death-lt4
loess_plot(
  data = fm_lt4, x = dd_percentile_lt4, y = death_90,
  x_point = dd_decile_lt4 * 10, y_point = death_rate_decile_lt4,
  title = "90-Day Mortality (Carboplatin AUC < 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "90-Day Mortality",
  vlines = pct_vlines_lt4
)
```

# 10 LOESS Plots: AE Rates by Actual Dose Discrepancy — AUC < 4 Cohort

## 10.1 Grade 2 Anemia (AUC < 4)

```{r}
#| label: plot-anemia-2-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = Anemia_g2_90days,
  title = "Grade >= 2 Anemia (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Anemia",
  vlines = raw_vlines
)
```

## 10.2 Grade 3 Anemia (AUC < 4)

```{r}
#| label: plot-anemia-3-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = Anemia_g3_90days,
  title = "Grade >= 3 Anemia (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Anemia",
  vlines = raw_vlines
)
```

## 10.3 Grade 2 Thrombocytopenia (AUC < 4)

```{r}
#| label: plot-throm-2-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = Throm_g2_90days,
  title = "Grade >= 2 Thrombocytopenia (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Thrombocytopenia",
  vlines = raw_vlines
)
```

## 10.4 Grade 3 Thrombocytopenia (AUC < 4)

```{r}
#| label: plot-throm-3-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = Throm_g3_90days,
  title = "Grade >= 3 Thrombocytopenia (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Thrombocytopenia",
  vlines = raw_vlines
)
```

## 10.5 Grade 2 AKI (AUC < 4)

```{r}
#| label: plot-aki-2-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = AKI_g2_90days,
  title = "Grade >= 2 Creatinine Increased (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Creatinine Increased",
  vlines = raw_vlines
)
```

## 10.6 Grade 3 AKI (AUC < 4)

```{r}
#| label: plot-aki-3-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = AKI_g3_90days,
  title = "Grade >= 3 Creatinine Increased (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Creatinine Increased",
  vlines = raw_vlines
)
```

## 10.7 Overall Hospitalization (AUC < 4)

```{r}
#| label: plot-hosp-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = hosp_90,
  title = "Overall Hospitalization (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Overall Hospitalization",
  vlines = raw_vlines
)
```

## 10.8 Platinum-Related Hospitalization (AUC < 4)

```{r}
#| label: plot-platinum-hosp-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = platinum_related_hosp,
  title = "Hospitalization for Platinum-Associated AEs (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Hospitalization for Platinum-Associated AEs",
  vlines = raw_vlines
)
```

## 10.9 90-Day Death (AUC < 4)

```{r}
#| label: plot-death-raw-lt4
loess_plot_raw(
  data = fm_lt4, x = dose_discrepancy, y = death_90,
  title = "90-Day Mortality (Carboplatin AUC < 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "90-Day Mortality",
  vlines = raw_vlines
)
```

# 11 Fine-Gray Competing Risk Regression Models

Adjusted for covariates from the reference analysis (excluding `egfr_cock`):
`age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score`.
Anemia models add `pre_HGB_45days`; thrombocytopenia models add `pre_PLT_45days`;
composite grade 2/3 AE models add both.

## 11.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.2 Grade 2 Anemia

```{r}
#| label: fg-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.3 Grade 3 Anemia

```{r}
#| label: fg-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.6 Grade 2 AKI

```{r}
#| label: fg-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.7 Grade 3 AKI

```{r}
#| label: fg-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.8 Composite Grade 2 AEs

```{r}
#| label: fg-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 11.9 Composite Grade 3 AEs

```{r}
#| label: fg-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 12 Fine-Gray Models: Dose Discrepancy > 50 mg

Same models as Section 11, using `dd_gt50` as the exposure.

## 12.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg50-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.2 Grade 2 Anemia

```{r}
#| label: fg50-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.3 Grade 3 Anemia

```{r}
#| label: fg50-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg50-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg50-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.6 Grade 2 AKI

```{r}
#| label: fg50-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.7 Grade 3 AKI

```{r}
#| label: fg50-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.8 Composite Grade 2 AEs

```{r}
#| label: fg50-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 12.9 Composite Grade 3 AEs

```{r}
#| label: fg50-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 13 Cox Proportional Hazards Models: 90-Day Death

Death is the terminal event (no competing risk), so we use standard Cox PH regression
with the same covariate adjustment as the Fine-Gray models above.

## 13.1 Cox for Death — dd_gt25

```{r}
#| label: cox-death-dd25
library(survival)
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 13.2 Cox for Death — dd_gt50

```{r}
#| label: cox-death-dd50
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 14 LOESS Plots: Carboplatin AUC >= 4 Cohort (Percentile)

```{r}
#| label: carbo-ge4-subset
# Subset to carboplatin patients with AUC >= 4
fm_ge4 <- final_master %>%
  filter(carbo_AUC_cat != "<4")

# Recompute percentile and decile within this subset
fm_ge4 <- fm_ge4 %>%
  mutate(
    dd_percentile_ge4 = ntile(dose_discrepancy, 100),
    dd_decile_ge4     = ntile(dose_discrepancy, 10)
  ) %>%
  group_by(dd_decile_ge4) %>%
  mutate(
    anemia_2_rate_decile_ge4             = mean(Anemia_g2_90days, na.rm = TRUE),
    anemia_3_rate_decile_ge4             = mean(Anemia_g3_90days, na.rm = TRUE),
    throm_2_rate_decile_ge4              = mean(Throm_g2_90days, na.rm = TRUE),
    throm_3_rate_decile_ge4              = mean(Throm_g3_90days, na.rm = TRUE),
    aki_2_rate_decile_ge4                = mean(AKI_g2_90days, na.rm = TRUE),
    aki_3_rate_decile_ge4                = mean(AKI_g3_90days, na.rm = TRUE),
    hos_rate_decile_ge4                  = mean(hosp_90, na.rm = TRUE),
    platinum_related_hos_rate_decile_ge4 = mean(platinum_related_hosp, na.rm = TRUE),
    death_rate_decile_ge4                = mean(death_90, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(dd_decile_ge4 = as.numeric(dd_decile_ge4))
```

```{r}
#| label: carbo-ge4-vlines
# Median dose discrepancy at P60 and P70 within the AUC >= 4 subset
median_dd_p60_ge4 <- median(
  fm_ge4$dose_discrepancy[fm_ge4$dd_percentile_ge4 == 60], na.rm = TRUE)
median_dd_p70_ge4 <- median(
  fm_ge4$dose_discrepancy[fm_ge4$dd_percentile_ge4 == 70], na.rm = TRUE)

pct_vlines_ge4 <- data.frame(
  x     = c(60, 70),
  label = c(paste0("median: ", round(median_dd_p60_ge4, 0), ""),
            paste0("median: ", round(median_dd_p70_ge4, 0), ""))
)
```

## 14.1 Grade 2 Anemia (AUC >= 4)

```{r}
#| label: plot-anemia-2-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = Anemia_g2_90days,
  x_point = dd_decile_ge4 * 10, y_point = anemia_2_rate_decile_ge4,
  title = "Grade >= 2 Anemia (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Anemia",
  vlines = pct_vlines_ge4
)
```

## 14.2 Grade 3 Anemia (AUC >= 4)

```{r}
#| label: plot-anemia-3-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = Anemia_g3_90days,
  x_point = dd_decile_ge4 * 10, y_point = anemia_3_rate_decile_ge4,
  title = "Grade >= 3 Anemia (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Anemia",
  vlines = pct_vlines_ge4
)
```

## 14.3 Grade 2 Thrombocytopenia (AUC >= 4)

```{r}
#| label: plot-throm-2-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = Throm_g2_90days,
  x_point = dd_decile_ge4 * 10, y_point = throm_2_rate_decile_ge4,
  title = "Grade >= 2 Thrombocytopenia (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Thrombocytopenia",
  vlines = pct_vlines_ge4
)
```

## 14.4 Grade 3 Thrombocytopenia (AUC >= 4)

```{r}
#| label: plot-throm-3-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = Throm_g3_90days,
  x_point = dd_decile_ge4 * 10, y_point = throm_3_rate_decile_ge4,
  title = "Grade >= 3 Thrombocytopenia (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Thrombocytopenia",
  vlines = pct_vlines_ge4
)
```

## 14.5 Grade 2 AKI (AUC >= 4)

```{r}
#| label: plot-aki-2-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = AKI_g2_90days,
  x_point = dd_decile_ge4 * 10, y_point = aki_2_rate_decile_ge4,
  title = "Grade >= 2 Creatinine Increased (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Creatinine Increased",
  vlines = pct_vlines_ge4
)
```

## 14.6 Grade 3 AKI (AUC >= 4)

```{r}
#| label: plot-aki-3-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = AKI_g3_90days,
  x_point = dd_decile_ge4 * 10, y_point = aki_3_rate_decile_ge4,
  title = "Grade >= 3 Creatinine Increased (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Creatinine Increased",
  vlines = pct_vlines_ge4
)
```

## 14.7 Overall Hospitalization (AUC >= 4)

```{r}
#| label: plot-hosp-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = hosp_90,
  x_point = dd_decile_ge4 * 10, y_point = hos_rate_decile_ge4,
  title = "Overall Hospitalization (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Overall Hospitalization",
  vlines = pct_vlines_ge4
)
```

## 14.8 Platinum-Related Hospitalization (AUC >= 4)

```{r}
#| label: plot-platinum-hosp-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = platinum_related_hosp,
  x_point = dd_decile_ge4 * 10, y_point = platinum_related_hos_rate_decile_ge4,
  title = "Hospitalization for Platinum-Associated AEs (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Hospitalization for Platinum-Associated AEs",
  vlines = pct_vlines_ge4
)
```

## 14.9 90-Day Death (AUC >= 4)

```{r}
#| label: plot-death-ge4
loess_plot(
  data = fm_ge4, x = dd_percentile_ge4, y = death_90,
  x_point = dd_decile_ge4 * 10, y_point = death_rate_decile_ge4,
  title = "90-Day Mortality (Carboplatin AUC >= 4)",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "90-Day Mortality",
  vlines = pct_vlines_ge4
)
```

# 15 LOESS Plots: AE Rates by Actual Dose Discrepancy — AUC >= 4 Cohort

## 15.1 Grade 2 Anemia (AUC >= 4)

```{r}
#| label: plot-anemia-2-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = Anemia_g2_90days,
  title = "Grade >= 2 Anemia (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Anemia",
  vlines = raw_vlines
)
```

## 15.2 Grade 3 Anemia (AUC >= 4)

```{r}
#| label: plot-anemia-3-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = Anemia_g3_90days,
  title = "Grade >= 3 Anemia (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Anemia",
  vlines = raw_vlines
)
```

## 15.3 Grade 2 Thrombocytopenia (AUC >= 4)

```{r}
#| label: plot-throm-2-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = Throm_g2_90days,
  title = "Grade >= 2 Thrombocytopenia (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Thrombocytopenia",
  vlines = raw_vlines
)
```

## 15.4 Grade 3 Thrombocytopenia (AUC >= 4)

```{r}
#| label: plot-throm-3-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = Throm_g3_90days,
  title = "Grade >= 3 Thrombocytopenia (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Thrombocytopenia",
  vlines = raw_vlines
)
```

## 15.5 Grade 2 AKI (AUC >= 4)

```{r}
#| label: plot-aki-2-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = AKI_g2_90days,
  title = "Grade >= 2 Creatinine Increased (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Creatinine Increased",
  vlines = raw_vlines
)
```

## 15.6 Grade 3 AKI (AUC >= 4)

```{r}
#| label: plot-aki-3-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = AKI_g3_90days,
  title = "Grade >= 3 Creatinine Increased (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Creatinine Increased",
  vlines = raw_vlines
)
```

## 15.7 Overall Hospitalization (AUC >= 4)

```{r}
#| label: plot-hosp-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = hosp_90,
  title = "Overall Hospitalization (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Overall Hospitalization",
  vlines = raw_vlines
)
```

## 15.8 Platinum-Related Hospitalization (AUC >= 4)

```{r}
#| label: plot-platinum-hosp-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = platinum_related_hosp,
  title = "Hospitalization for Platinum-Associated AEs (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Hospitalization for Platinum-Associated AEs",
  vlines = raw_vlines
)
```

## 15.9 90-Day Death (AUC >= 4)

```{r}
#| label: plot-death-raw-ge4
loess_plot_raw(
  data = fm_ge4, x = dose_discrepancy, y = death_90,
  title = "90-Day Mortality (Carboplatin AUC >= 4)",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "90-Day Mortality",
  vlines = raw_vlines
)
```

# 16 Fine-Gray Competing Risk Models: AUC >= 4, dd_gt25

Same covariate adjustment as Section 11, restricted to carboplatin AUC >= 4 patients.

## 16.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg-ge4-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.2 Grade 2 Anemia

```{r}
#| label: fg-ge4-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.3 Grade 3 Anemia

```{r}
#| label: fg-ge4-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg-ge4-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg-ge4-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.6 Grade 2 AKI

```{r}
#| label: fg-ge4-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.7 Grade 3 AKI

```{r}
#| label: fg-ge4-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.8 Composite Grade 2 AEs

```{r}
#| label: fg-ge4-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.9 Composite Grade 3 AEs

```{r}
#| label: fg-ge4-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 16.10 Cox for Death — dd_gt25 (AUC >= 4)

```{r}
#| label: cox-ge4-death-dd25
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 17 Fine-Gray Competing Risk Models: AUC >= 4, dd_gt50

Same models as Section 16, using `dd_gt50` as the exposure.

## 17.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg50-ge4-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.2 Grade 2 Anemia

```{r}
#| label: fg50-ge4-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.3 Grade 3 Anemia

```{r}
#| label: fg50-ge4-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg50-ge4-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg50-ge4-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.6 Grade 2 AKI

```{r}
#| label: fg50-ge4-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.7 Grade 3 AKI

```{r}
#| label: fg50-ge4-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.8 Composite Grade 2 AEs

```{r}
#| label: fg50-ge4-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.9 Composite Grade 3 AEs

```{r}
#| label: fg50-ge4-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 17.10 Cox for Death — dd_gt50 (AUC >= 4)

```{r}
#| label: cox-ge4-death-dd50
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score,
  data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 18 Fine-Gray Models with Cockcroft-Gault: dd_gt25

Same models as Section 11 with `cockcroft` added as a covariate.

## 18.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg-cg-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.2 Grade 2 Anemia

```{r}
#| label: fg-cg-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.3 Grade 3 Anemia

```{r}
#| label: fg-cg-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg-cg-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg-cg-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.6 Grade 2 AKI

```{r}
#| label: fg-cg-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.7 Grade 3 AKI

```{r}
#| label: fg-cg-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.8 Composite Grade 2 AEs

```{r}
#| label: fg-cg-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.9 Composite Grade 3 AEs

```{r}
#| label: fg-cg-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 18.10 Cox for Death — dd_gt25

```{r}
#| label: cox-cg-death-dd25
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 19 Fine-Gray Models with Cockcroft-Gault: dd_gt50

Same models as Section 18, using `dd_gt50` as the exposure.

## 19.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg50-cg-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.2 Grade 2 Anemia

```{r}
#| label: fg50-cg-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.3 Grade 3 Anemia

```{r}
#| label: fg50-cg-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg50-cg-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg50-cg-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.6 Grade 2 AKI

```{r}
#| label: fg50-cg-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.7 Grade 3 AKI

```{r}
#| label: fg50-cg-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.8 Composite Grade 2 AEs

```{r}
#| label: fg50-cg-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.9 Composite Grade 3 AEs

```{r}
#| label: fg50-cg-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 19.10 Cox for Death — dd_gt50

```{r}
#| label: cox-cg-death-dd50
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  data = final_master
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 20 Fine-Gray Models with Cockcroft-Gault: AUC >= 4, dd_gt25

Same models as Section 18, restricted to carboplatin AUC >= 4 patients.

## 20.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg-cg-ge4-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.2 Grade 2 Anemia

```{r}
#| label: fg-cg-ge4-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.3 Grade 3 Anemia

```{r}
#| label: fg-cg-ge4-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg-cg-ge4-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg-cg-ge4-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.6 Grade 2 AKI

```{r}
#| label: fg-cg-ge4-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.7 Grade 3 AKI

```{r}
#| label: fg-cg-ge4-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.8 Composite Grade 2 AEs

```{r}
#| label: fg-cg-ge4-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.9 Composite Grade 3 AEs

```{r}
#| label: fg-cg-ge4-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 20.10 Cox for Death — dd_gt25 (AUC >= 4)

```{r}
#| label: cox-cg-ge4-death-dd25
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt25 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 21 Fine-Gray Models with Cockcroft-Gault: AUC >= 4, dd_gt50

Same models as Section 20, using `dd_gt50` as the exposure.

## 21.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: fg50-cg-ge4-side-effect
tidycmprsk::crr(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.2 Grade 2 Anemia

```{r}
#| label: fg50-cg-ge4-anemia-2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.3 Grade 3 Anemia

```{r}
#| label: fg50-cg-ge4-anemia-3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.4 Grade 2 Thrombocytopenia

```{r}
#| label: fg50-cg-ge4-throm-2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.5 Grade 3 Thrombocytopenia

```{r}
#| label: fg50-cg-ge4-throm-3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.6 Grade 2 AKI

```{r}
#| label: fg50-cg-ge4-aki-2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.7 Grade 3 AKI

```{r}
#| label: fg50-cg-ge4-aki-3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.8 Composite Grade 2 AEs

```{r}
#| label: fg50-cg-ge4-grade-2-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.9 Composite Grade 3 AEs

```{r}
#| label: fg50-cg-ge4-grade-3-aes
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days + cockcroft,
  failcode = 1, data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 21.10 Cox for Death — dd_gt50 (AUC >= 4)

```{r}
#| label: cox-cg-ge4-death-dd50
coxph(
  Surv(time_to_death_90, death_90) ~ dd_gt50 + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + cockcroft,
  data = fm_ge4
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```
