---
title: "Sherley Project — Carboplatin Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-jx-carbo
# Force UTF-8 locale so kable captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)
library(flextable)
library(officer)
library(rvg)

# Output directory for downloadable Word tables (placed under docs/ so the
# rendered website can serve them from ../tables/carbo/<name>.docx).
docx_dir <- "docs/tables/carbo"
dir.create(docx_dir, recursive = TRUE, showWarnings = FALSE)

# Output directory for downloadable PowerPoint plots (../plots/carbo/<name>.pptx).
# Use absolute path so fig.process hook (which may run from a different
# working directory than the chunks themselves) still resolves correctly.
pptx_dir <- normalizePath("docs/plots/carbo", winslash = "/", mustWork = FALSE)
dir.create(pptx_dir, recursive = TRUE, showWarnings = FALSE)

save_tbl_docx <- function(tbl, docx_name) {
  ft <- gtsummary::as_flex_table(tbl)
  flextable::save_as_docx(ft, path = file.path(docx_dir,
                                               paste0(docx_name, ".docx")))
  invisible(tbl)
}

# Save the given ggplot as an editable PowerPoint slide via rvg::dml.
# The chunk label (from knitr::opts_current) is used as the filename so each
# chunk produces a uniquely-named pptx in docs/plots/carbo/. Returns NULL on
# failure (officer/rvg missing, ggplot invalid, etc.). Plot helpers below
# call this directly; for inline ggplot chunks the fig.process hook below
# also runs it on ggplot2::last_plot() as a safety net.
.save_plot_pptx <- function(p, name = NULL) {
  if (is.null(p) || !inherits(p, "ggplot")) return(invisible(NULL))
  if (is.null(name)) {
    name <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  }
  if (is.null(name)) return(invisible(NULL))
  safe <- gsub("[^A-Za-z0-9]+", "_", name)
  out  <- file.path(pptx_dir, paste0(safe, ".pptx"))
  ok <- tryCatch({
    pp <- officer::read_pptx()
    pp <- officer::add_slide(pp, layout = "Title and Content", master = "Office Theme")
    pp <- officer::ph_with(
      pp,
      value = rvg::dml(ggobj = p),
      location = officer::ph_location_type(type = "body")
    )
    print(pp, target = out)
    TRUE
  }, error = function(e) FALSE)
  invisible(if (ok) paste0("../plots/carbo/", safe, ".pptx") else NULL)
}

# Safety-net fig.process hook: after each chunk's figure is saved as PNG,
# also save ggplot2::last_plot() as .pptx. Plot helpers also call
# .save_plot_pptx directly inside their bodies; this hook covers inline-
# ggplot chunks (eGFR histogram, dose-distribution, etc.) that don't go
# through a helper. Safe to double-save — same chunk label, same target file.
knitr::opts_chunk$set(fig.process = function(file_path) {
  lbl <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  if (!is.null(lbl)) {
    p <- tryCatch(ggplot2::last_plot(), error = function(e) NULL)
    if (!is.null(p) && inherits(p, "ggplot")) {
      .save_plot_pptx(p, lbl)
    }
  }
  file_path
})

# Per-plot download links are injected after render by the post-render
# script scripts/inject_pptx_links.py (configured in _quarto.yml). It
# scans each rendered HTML page, finds every figure-html <img> whose
# basename matches a .pptx slug in docs/plots/carbo/, and inserts a
# small "📥 Download editable PowerPoint" link beneath the figure.
# (We tried doing this inside R via knitr hooks, but Quarto's HTML
# pipeline bypasses both the plot and chunk hooks, so a post-render
# pass on the HTML is the reliable path.)

# Fallback renderers for when a model fit fails (singular design matrix etc.)
# on the small Sherley sub-cohort. Used by tryCatch wrappers in fg_model,
# csh_model, cox_model, and the plot_* helpers. Saves a placeholder pptx so
# the download index still lists the figure (so reviewers know which model
# could not be fit).
.plot_failed <- function(label = "Model could not be fit") {
  p <- ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = paste0(label, "\n(singular design — cohort too small)"),
             size = 3.5) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) +
    theme_void()
  .save_plot_pptx(p)
  p
}
.tbl_failed <- function() {
  knitr::asis_output(
    "> *Model could not be fit — design matrix is singular for this sub-cohort.*"
  )
}

# Load whole-cohort data, then keep only carboplatin patients
dat <- readRDS("sherley_final_master.rds") %>%
  filter(platin_group == "Carboplatin")

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
# Also create per-10 mL/min rescaled versions of cockcroft and CKD-EPI for
# reporting (HRs per 1 mL/min are clinically uninterpretable; convention in
# nephro-onc is per 10 mL/min — bio_agent confirmed). Adjusters keep raw scale.
dat <- dat %>%
  mutate(
    # Capped versions (for dose discrepancy calculations)
    cockcroft_cap125 = pmin(cockcroft, 125),
    # ckd_epi_gfr_cre_cys_unindex_cap125 already exists in data
    # Ratio uses UNCAPPED eGFR
    egfr_ratio    = ckd_epi_gfr_cre_cys_unindex / cockcroft,
    egfr_ratio_per10 = -egfr_ratio * 10,  # per 0.1-unit *decrease* reporting scale
    egfr_discrepancy = ckd_epi_gfr_cre_cys_unindex - cockcroft,
    # Dose discrepancy uses CAPPED eGFR (already computed in sherley_data.qmd)
    dose_discrep_per25increase = dose_discrepancy / 25,
    abs_dose_discrep = abs(dose_discrepancy),
    abs_dose_discrep_cat = cut(abs_dose_discrep,
      breaks = c(0, 25, 50, 75, 100, Inf),
      labels = c("<25", "25-49.99", "50-74.99", "75-99.99", ">=100"),
      right = FALSE, include.lowest = TRUE),
    # Binary exposure for adjusted CIF curves (Section 14): 1 if patient was
    # over-dosed by 25 mg or more (actual - predicted >= 25), else 0.
    dose_discrep_ge25 = as.integer(dose_discrepancy >= 25),
    # Signed dose discrepancy = actual - predicted; 10 bins symmetric around 0.
    signed_dose_discrep_cat = cut(dose_discrepancy,
      breaks = c(-Inf, -100, -75, -50, -25, 0, 25, 50, 75, 100, Inf),
      labels = c("<=-100", "-99.99 to -75", "-74.99 to -50",
                 "-49.99 to -25", "-24.99 to 0",
                 "0 to 24.99", "25 to 49.99", "50 to 74.99",
                 "75 to 99.99", ">=100"),
      right = FALSE, include.lowest = TRUE),
    cockcroft_per10 = cockcroft / 10,
    ckd_epi_per10   = ckd_epi_gfr_cre_cys_unindex / 10
  )

cat("Carboplatin cohort N =", nrow(dat), "\n")
```

# 2 Dose Distribution (Carboplatin)

## 2.1 Actual vs Predicted Dose

```{r}
#| label: jx-carbo-dose-overlay
#| fig-width: 8
#| fig-height: 5
dose_long <- dat %>%
  select(record_id, carbo_dose_redcap, carbo_dose_cre_cys) %>%
  pivot_longer(
    cols = c(carbo_dose_redcap, carbo_dose_cre_cys),
    names_to = "dose_type", values_to = "dose_mg"
  ) %>%
  filter(!is.na(dose_mg)) %>%
  mutate(dose_type = case_match(dose_type,
    "carbo_dose_redcap"  ~ "Actual (REDCap)",
    "carbo_dose_cre_cys" ~ "Predicted (CKD-EPI Cr-Cys)"
  ))

ggplot(dose_long, aes(x = dose_mg, fill = dose_type)) +
  geom_histogram(alpha = 0.5, bins = 40, position = "identity", color = "black") +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution",
       x = "Dose (mg)", y = "Number of Patients", fill = "Dose Type") +
  theme_minimal(base_size = 14)
```

## 2.2 Signed Dose Discrepancy Distribution

Smooth kernel density estimate of the signed dose discrepancy (actual − predicted, CKD-EPI Cr-Cys). The area under the curve is shaded by sign — negative (under-dosed region) on one side, positive on the other.

```{r}
#| label: jx-carbo-dose-discrep-hist
#| fig-width: 9
#| fig-height: 5
dose_vals <- dat %>%
  filter(!is.na(dose_discrepancy)) %>%
  pull(dose_discrepancy)

dens <- density(dose_vals, n = 512)
y_at_zero <- approx(dens$x, dens$y, xout = 0)$y

dens_df <- tibble(x = dens$x, y = dens$y) %>%
  bind_rows(tibble(x = 0, y = y_at_zero)) %>%
  arrange(x)

neg_part <- dens_df %>% filter(x <= 0) %>% mutate(side = "neg")
pos_part <- dens_df %>% filter(x >= 0) %>% mutate(side = "pos")
plot_df  <- bind_rows(neg_part, pos_part)

ggplot() +
  geom_area(data = plot_df, aes(x = x, y = y, fill = side), alpha = 0.6) +
  geom_line(data = dens_df, aes(x = x, y = y), linewidth = 0.6, color = "black") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey40") +
  scale_fill_manual(values = c(neg = "#E31A1C", pos = "#1F78B4"),
                    guide = "none") +
  coord_cartesian(xlim = c(-250, 250)) +
  labs(title = "Distribution of Signed Dose Discrepancy (Carboplatin)",
       x = "Dose Discrepancy (mg) = actual - predicted",
       y = "Density") +
  theme_minimal(base_size = 13)
```

# 3 Table 1: Baseline Characteristics (Carboplatin Only)

```{r}
#| label: jx-table1-carbo
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    carbo_AUC, carbo_AUC_cat,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, other_chemo, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, score, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

# 4 eGFR Ratio Distribution (Carboplatin)

```{r}
#| label: jx-carbo-egfr-ratio-hist
#| fig-width: 8
#| fig-height: 5
ratio_hist <- dat %>% filter(!is.na(egfr_ratio))

ggplot(ratio_hist, aes(x = egfr_ratio)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count)) * 100),
                 binwidth = 0.1, boundary = 0,
                 fill = "steelblue", color = "black", alpha = 0.7) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  labs(title = "Distribution of eGFR Ratio (Carboplatin)",
       x = "eGFR Ratio",
       y = "Percent of Patients (%)") +
  scale_x_continuous(breaks = seq(0, 3, 0.2)) +
  theme_minimal(base_size = 14)
```

# Event Counts by Outcome (Diagnostic)

For each outcome the table below shows the cohort N, events (status = 1 within 90 days), competing deaths (status = 2; not applicable to 90-day death which is modelled by Cox PH), censored, event rate, and events-per-variable (EPV) using the **5-variable adjuster set** for this cohort (`age`, `sex`, `ecog_score` (ECOG performance status, numeric 0–5), `ici`, `cockcroft` (creatinine clearance)). As a rule of thumb, Fine-Gray fits need **≥ 5 × adj** events to be stable; **< 2 × adj** almost always produces a singular design matrix, which is why the helper functions in this file fall back to a "Model could not be fit" placeholder where you see one.

```{r}
#| label: jx-event-counts-carbo
.outcomes_tbl <- function(dat, cohort_label, n_adj = 5) {
  sumrow <- function(label, status_var, is_cox = FALSE) {
    s <- suppressWarnings(as.integer(as.character(dat[[status_var]])))
    n_total     <- sum(!is.na(s))
    n_event     <- sum(s == 1, na.rm = TRUE)
    n_compdeath <- if (is_cox) NA_integer_ else sum(s == 2, na.rm = TRUE)
    n_cens      <- sum(s == 0, na.rm = TRUE)
    epv         <- if (n_total > 0) n_event / n_adj else NA_real_
    fit_likely  <- if (is.na(epv))                "—"
                   else if (n_event >= 5 * n_adj) "✓ likely OK"
                   else if (n_event >= 2 * n_adj) "marginal"
                   else                           "✗ singular likely"
    tibble::tibble(
      Outcome            = label,
      N                  = n_total,
      Events             = n_event,
      `Competing deaths` = n_compdeath,
      Censored           = n_cens,
      `Event rate`       = if (n_total > 0) sprintf("%.1f%%", 100 * n_event / n_total) else "—",
      EPV                = if (!is.na(epv)) sprintf("%.1f", epv) else "—",
      `Fit reliable?`    = fit_likely
    )
  }
  dplyr::bind_rows(
    sumrow("Anemia Grade 2",                   "cmp_status_anemia_2"),
    sumrow("Anemia Grade 3",                   "cmp_status_anemia_3"),
    sumrow("Thrombocytopenia Grade 2",         "cmp_status_throm_2"),
    sumrow("Thrombocytopenia Grade 3",         "cmp_status_throm_3"),
    sumrow("AKI Grade 2",                      "cmp_status_aki_2"),
    sumrow("AKI (KDIGO)",                      "cmp_status_aki_kdigo"),
    sumrow("Composite Grade 2 AEs",            "cmp_status_grade_2_aes"),
    sumrow("Composite Grade 3 AEs",            "cmp_status_grade_3_aes"),
    sumrow("Overall Hospitalization",          "cmp_status_any_hosp"),
    sumrow("Platinum-Related Hospitalization", "cmp_status_side_effect"),
    sumrow("90-Day Death (Cox PH)",            "death_90", is_cox = TRUE)
  )
}

knitr::kable(
  .outcomes_tbl(dat, "carboplatin cohort"),
  align = c("l","r","r","r","r","r","r","l"),
  caption = sprintf(
    "Event counts for the **carboplatin cohort** (N = %d). EPV uses 5 adjusters (age, sex, ecog_score, ici, cockcroft).",
    nrow(dat)
  )
)
```

# 5 Fine-Gray Models — eGFR Ratio (Carboplatin)

Each table below shows univariable (one variable at a time) and multivariable Fine-Gray subdistribution hazard ratios side-by-side. A Word version of every table is saved during render — click any link below to download:

- [Anemia Grade 2](../tables/carbo/sec5_anemia_2.docx) · [Anemia Grade 3](../tables/carbo/sec5_anemia_3.docx)
- [Thrombocytopenia Grade 2](../tables/carbo/sec5_throm_2.docx) · [Thrombocytopenia Grade 3](../tables/carbo/sec5_throm_3.docx)
- [AKI Grade 2](../tables/carbo/sec5_aki_2.docx) · [AKI (KDIGO)](../tables/carbo/sec5_aki_kdigo.docx)
- [Composite Grade 2 AEs](../tables/carbo/sec5_grade_2_aes.docx) · [Composite Grade 3 AEs](../tables/carbo/sec5_grade_3_aes.docx)
- [Overall Hospitalization](../tables/carbo/sec5_any_hosp.docx) · [Platinum-Related Hospitalization](../tables/carbo/sec5_side_effect.docx)
- [90-Day Death (Cox PH)](../tables/carbo/sec5_death_90.docx)

```{r}
#| label: jx-carbo-fg-helper
.adj_set <- function(pre_labs, egfr_adj) {
  # Minimal adjuster set for the Sherley sub-cohort (N=169): the four
  # demographic/clinical confounders plus Cockcroft-Gault creatinine clearance.
  # The egfr_adj and pre_labs arguments are accepted for backward
  # compatibility but ignored.
  c("age", "sex", "ecog_score", "ici", "cockcroft")
}

# fg_model: returns univariable + multivariable merged Fine-Gray table.
# If docx_name is supplied, also saves the table as a .docx in docx_dir.
fg_model <- function(time_var, status_var, pred_var, pre_labs = NULL,
                     egfr_adj = c("none", "cockcroft", "ckd_epi"),
                     docx_name = NULL) {
  egfr_adj <- match.arg(egfr_adj)
  adj <- .adj_set(pre_labs, egfr_adj)
  all_vars <- c(pred_var, adj)

  fmla_mv <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(all_vars, collapse = " + ")
  ))
  tbl_mv <- tryCatch(
    tidycmprsk::crr(fmla_mv, failcode = 1, data = dat) %>%
      tbl_regression(exp = TRUE,
                     pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
      add_n(),
    error = function(e) NULL
  )

  y_call <- str2lang(sprintf("Surv(%s, %s)", time_var, status_var))
  tbl_uv <- tryCatch(
    rlang::inject(
      tbl_uvregression(
        data = dat,
        method = tidycmprsk::crr,
        y = !!y_call,
        include = dplyr::all_of(all_vars),
        exponentiate = TRUE,
        pvalue_fun = function(x) style_pvalue(x, digits = 3),
        method.args = list(failcode = 1)
      )
    ),
    error = function(e) NULL
  )

  if (is.null(tbl_uv) && is.null(tbl_mv)) {
    return(knitr::asis_output(
      "> *Model could not be fit — Fine-Gray design matrix is singular (insufficient events or collinear covariates for this sub-cohort).*"
    ))
  }

  out <- if (is.null(tbl_mv)) {
    tbl_uv
  } else if (is.null(tbl_uv)) {
    tbl_mv
  } else {
    tbl_merge(
      tbls = list(tbl_uv, tbl_mv),
      tab_spanner = c("**Univariable**", "**Multivariable**")
    )
  }

  if (!is.null(docx_name)) save_tbl_docx(out, docx_name)
  out
}

cox_model <- function(time_var, status_var, pred_var, pre_labs = NULL,
                      egfr_adj = c("none", "cockcroft", "ckd_epi"),
                      docx_name = NULL) {
  egfr_adj <- match.arg(egfr_adj)
  adj <- .adj_set(pre_labs, egfr_adj)
  all_vars <- c(pred_var, adj)

  fmla_mv <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(all_vars, collapse = " + ")
  ))
  tbl_mv <- survival::coxph(fmla_mv, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()

  y_call <- str2lang(sprintf("Surv(%s, %s)", time_var, status_var))
  tbl_uv <- rlang::inject(
    tbl_uvregression(
      data = dat,
      method = survival::coxph,
      y = !!y_call,
      include = dplyr::all_of(all_vars),
      exponentiate = TRUE,
      pvalue_fun = function(x) style_pvalue(x, digits = 3)
    )
  )

  out <- tbl_merge(
    tbls = list(tbl_uv, tbl_mv),
    tab_spanner = c("**Univariable**", "**Multivariable**")
  )

  if (!is.null(docx_name)) save_tbl_docx(out, docx_name)
  out
}
```

## 4.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-cg-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio_per10", "pre_HGB_45days", "cockcroft", docx_name = "sec5_anemia_2")
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-cg-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio_per10", "pre_HGB_45days", "cockcroft", docx_name = "sec5_anemia_3")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-cg-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio_per10", "pre_PLT_45days", "cockcroft", docx_name = "sec5_throm_2")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-cg-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio_per10", "pre_PLT_45days", "cockcroft", docx_name = "sec5_throm_3")
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-cg-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_aki_2")
```

## 4.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-fg-cg-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_aki_kdigo")
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-cg-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_grade_2_aes")
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-cg-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_grade_3_aes")
```

## 4.9 Overall Hospitalization

```{r}
#| label: jx-carbo-fg-cg-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_any_hosp")
```

## 4.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-fg-cg-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_side_effect")
```

## 4.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-cox-cg-death
cox_model("time_to_death_90", "death_90", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec5_death_90")
```

# 6 Cause-Specific Hazard Models — eGFR Ratio (Carboplatin)

```{r}
#| label: jx-carbo-csh-helper
csh_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  d <- dat
  d$csh_status <- ifelse(d[[status_var]] == 1, 1L, 0L)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", csh_status) ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  tryCatch(
    survival::coxph(fmla, data = d) %>%
      tbl_regression(exp = TRUE,
                     pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
      add_n(),
    error = function(e) .tbl_failed()
  )
}
```

## 5.1 Anemia Grade 2

```{r}
#| label: jx-carbo-csh-anemia2
csh_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio_per10", "pre_HGB_45days")
```

## 5.2 Anemia Grade 3

```{r}
#| label: jx-carbo-csh-anemia3
csh_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio_per10", "pre_HGB_45days")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-csh-throm2
csh_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio_per10", "pre_PLT_45days")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-csh-throm3
csh_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio_per10", "pre_PLT_45days")
```

## 5.5 AKI Grade 2

```{r}
#| label: jx-carbo-csh-aki2
csh_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio_per10")
```

## 5.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-csh-akikdigo
csh_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_ratio_per10")
```

## 5.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-csh-grade2
csh_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio_per10")
```

## 5.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-csh-grade3
csh_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio_per10")
```

## 5.9 Overall Hospitalization

```{r}
#| label: jx-carbo-csh-anyhosp
csh_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_ratio_per10")
```

## 5.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-csh-sideeffect
csh_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_ratio_per10")
```

## 5.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-csh-death
cox_model("time_to_death_90", "death_90", "egfr_ratio_per10", egfr_adj = "cockcroft")
```

# 7 Fine-Gray Models — Dose Discrepancy per 25 mg (Carboplatin)

## 7.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-dd-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "dose_discrep_per25increase", "pre_HGB_45days", "cockcroft")
```

## 7.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-dd-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "dose_discrep_per25increase", "pre_HGB_45days", "cockcroft")
```

## 7.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-dd-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "dose_discrep_per25increase", "pre_PLT_45days", "cockcroft")
```

## 7.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-dd-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "dose_discrep_per25increase", "pre_PLT_45days", "cockcroft")
```

## 7.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-dd-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 7.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-fg-dd-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 7.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-dd-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 7.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-dd-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 7.9 Overall Hospitalization

```{r}
#| label: jx-carbo-fg-dd-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 7.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-fg-dd-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 7.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-cox-dd-death
cox_model("time_to_death_90", "death_90", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

# 8 Cause-Specific Hazard Models — Dose Discrepancy per 25 mg (Carboplatin)

## 8.1 Anemia Grade 2

```{r}
#| label: jx-carbo-csh-dd-anemia2
csh_model("cmp_time_anemia_2", "cmp_status_anemia_2", "dose_discrep_per25increase", "pre_HGB_45days")
```

## 8.2 Anemia Grade 3

```{r}
#| label: jx-carbo-csh-dd-anemia3
csh_model("cmp_time_anemia_3", "cmp_status_anemia_3", "dose_discrep_per25increase", "pre_HGB_45days")
```

## 8.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-csh-dd-throm2
csh_model("cmp_time_throm_2", "cmp_status_throm_2", "dose_discrep_per25increase", "pre_PLT_45days")
```

## 8.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-csh-dd-throm3
csh_model("cmp_time_throm_3", "cmp_status_throm_3", "dose_discrep_per25increase", "pre_PLT_45days")
```

## 8.5 AKI Grade 2

```{r}
#| label: jx-carbo-csh-dd-aki2
csh_model("cmp_time_aki_2", "cmp_status_aki_2", "dose_discrep_per25increase")
```

## 8.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-csh-dd-akikdigo
csh_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "dose_discrep_per25increase")
```

## 8.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-csh-dd-grade2
csh_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "dose_discrep_per25increase")
```

## 8.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-csh-dd-grade3
csh_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "dose_discrep_per25increase")
```

## 8.9 Overall Hospitalization

```{r}
#| label: jx-carbo-csh-dd-anyhosp
csh_model("cmp_time_any_hosp", "cmp_status_any_hosp", "dose_discrep_per25increase")
```

## 8.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-csh-dd-sideeffect
csh_model("cmp_time_side_effect", "cmp_status_side_effect", "dose_discrep_per25increase")
```

## 8.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-csh-dd-death
cox_model("time_to_death_90", "death_90", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

::: {.callout-note}
## Why anchor at the median (subHR = 1 at the reference)

Three reasons to anchor at the **median**:

1. **Interpretability**: "A patient with eGFR ratio of 0.8 has ~1.5× the subHR compared to a typical patient (at the median)."
2. **Stability**: The median sits in the densest part of the data, so estimates near it have the tightest confidence intervals. The CIs fan out as you move away — you can see this in the plots.
3. **No arbitrary choice**: If we picked 1.0 arbitrarily, the plot would look almost identical here (because median ≈ 1), but in cohorts where the median is 0.9 or 1.1, picking 1.0 would either shift or distort the curve without changing the actual model.
:::

# 9 Linear subHR Curves — eGFR Ratio (raw scale) (Carboplatin)

```{r}
#| label: jx-carbo-linsubhr-ratio-helper
plot_subhr_linear_ratio <- function(time_var, status_var, extra_adj = NULL,
                                    outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_ratio = d$egfr_ratio, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- tryCatch(
    cmprsk::crr(ftime = time_num, fstatus = stat_num,
                cov1 = X, failcode = 1),
    error = function(e) NULL
  )
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]

  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_ratio, 0.025, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "CKD-EPI Cr-Cys / CG ratio",
         y = "subHR (95% CI)",
         title = outcome_label) +
    coord_cartesian(xlim = c(0.65, 1.45), ylim = c(0, 4)) +
    theme_minimal(base_size = 11) -> p
  .save_plot_pptx(p)
  p
}

plot_cox_linear_ratio <- function(time_var, status_var, extra_adj = NULL,
                                  outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_ratio + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- tryCatch(survival::coxph(fmla, data = d), error = function(e) NULL)
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- coef(fit)["egfr_ratio"]
  V_beta <- vcov(fit)["egfr_ratio", "egfr_ratio"]

  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_ratio, 0.025, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "CKD-EPI Cr-Cys / CG ratio",
         y = "HR (95% CI)",
         title = outcome_label) +
    coord_cartesian(xlim = c(0.65, 1.45), ylim = c(0, 4)) +
    theme_minimal(base_size = 11) -> p
  .save_plot_pptx(p)
  p
}
```

## 9.1 Anemia Grade 2

```{r}
#| label: jx-carbo-linsubhr-ratio-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_anemia_2", "cmp_status_anemia_2",
                        "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 9.2 Anemia Grade 3

```{r}
#| label: jx-carbo-linsubhr-ratio-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_anemia_3", "cmp_status_anemia_3",
                        "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 9.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-linsubhr-ratio-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_throm_2", "cmp_status_throm_2",
                        "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 9.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-linsubhr-ratio-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_throm_3", "cmp_status_throm_3",
                        "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 9.5 AKI Grade 2

```{r}
#| label: jx-carbo-linsubhr-ratio-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_aki_2", "cmp_status_aki_2",
                        NULL, "AKI Grade 2 (Carboplatin)")
```

## 9.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-linsubhr-ratio-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                        NULL, "AKI (KDIGO) (Carboplatin)")
```

## 9.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-linsubhr-ratio-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                        NULL, "Composite Grade 2 AEs (Carboplatin)")
```

## 9.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-linsubhr-ratio-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                        NULL, "Composite Grade 3 AEs (Carboplatin)")
```

## 9.9 Overall Hospitalization

```{r}
#| label: jx-carbo-linsubhr-ratio-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_any_hosp", "cmp_status_any_hosp",
                        NULL, "Overall Hospitalization (Carboplatin)")
```

## 9.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-linsubhr-ratio-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_side_effect", "cmp_status_side_effect",
                        NULL, "Platinum-Related Hospitalization (Carboplatin)")
```

## 9.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-cox-linear-ratio-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear_ratio("time_to_death_90", "death_90",
                      NULL, "90-Day Death (Cox PH) (Carboplatin)")
```

# 10 Linear subHR Curves — eGFR Discrepancy (raw scale) (Carboplatin)

```{r}
#| label: jx-carbo-linsubhr-disc-egfr-helper
plot_subhr_linear_egfrdisc <- function(time_var, status_var, extra_adj = NULL,
                                       outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("egfr_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_discrepancy = d$egfr_discrepancy, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- tryCatch(
    cmprsk::crr(ftime = time_num, fstatus = stat_num,
                cov1 = X, failcode = 1),
    error = function(e) NULL
  )
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_discrepancy, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_discrepancy, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr1   <- exp(beta);             hr1_l <- exp(beta - 1.96 * se_b);             hr1_u <- exp(beta + 1.96 * se_b)
  hri   <- exp(beta * iqr_w);     hri_l <- exp(beta * iqr_w - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(beta * iqr_w + 1.96 * abs(iqr_w) * se_b)
  subtitle_str <- sprintf(
    "subHR per 1 mL/min: %.2f (%.2f-%.2f)  |  per IQR (Δ = %.1f): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f]",
    hr1, hr1_l, hr1_u, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$egfr_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "eGFR Discrepancy (mL/min)",
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25")) -> p
  .save_plot_pptx(p)
  p
}

plot_cox_linear_egfrdisc <- function(time_var, status_var, extra_adj = NULL,
                                     outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("egfr_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_discrepancy + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- tryCatch(survival::coxph(fmla, data = d), error = function(e) NULL)
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- coef(fit)["egfr_discrepancy"]
  V_beta <- vcov(fit)["egfr_discrepancy", "egfr_discrepancy"]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_discrepancy, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_discrepancy, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr1   <- exp(beta);             hr1_l <- exp(beta - 1.96 * se_b);             hr1_u <- exp(beta + 1.96 * se_b)
  hri   <- exp(beta * iqr_w);     hri_l <- exp(beta * iqr_w - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(beta * iqr_w + 1.96 * abs(iqr_w) * se_b)
  subtitle_str <- sprintf(
    "HR per 1 mL/min: %.2f (%.2f-%.2f)  |  per IQR (Δ = %.1f): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f]",
    hr1, hr1_l, hr1_u, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$egfr_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "eGFR Discrepancy (mL/min)",
         y = "HR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25")) -> p
  .save_plot_pptx(p)
  p
}
```

## 10.1 Anemia Grade 2

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_anemia_2", "cmp_status_anemia_2",
                           "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 10.2 Anemia Grade 3

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_anemia_3", "cmp_status_anemia_3",
                           "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 10.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_throm_2", "cmp_status_throm_2",
                           "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 10.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_throm_3", "cmp_status_throm_3",
                           "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 10.5 AKI Grade 2

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_aki_2", "cmp_status_aki_2",
                           NULL, "AKI Grade 2 (Carboplatin)")
```

## 10.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                           NULL, "AKI (KDIGO) (Carboplatin)")
```

## 10.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                           NULL, "Composite Grade 2 AEs (Carboplatin)")
```

## 10.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                           NULL, "Composite Grade 3 AEs (Carboplatin)")
```

## 10.9 Overall Hospitalization

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_any_hosp", "cmp_status_any_hosp",
                           NULL, "Overall Hospitalization (Carboplatin)")
```

## 10.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_side_effect", "cmp_status_side_effect",
                           NULL, "Platinum-Related Hospitalization (Carboplatin)")
```

## 10.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-linsubhr-egfrdisc-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear_egfrdisc("time_to_death_90", "death_90",
                         NULL, "90-Day Death (Cox PH) (Carboplatin)")
```

# 11 Linear subHR Curves — Dose Discrepancy (raw scale) (Carboplatin)

```{r}
#| label: jx-carbo-linsubhr-dosedisc-helper
plot_subhr_linear <- function(time_var, status_var, extra_adj = NULL,
                              outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(dose_discrepancy = d$dose_discrepancy, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- tryCatch(
    cmprsk::crr(ftime = time_num, fstatus = stat_num,
                cov1 = X, failcode = 1),
    error = function(e) NULL
  )
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]

  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$dose_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "Dose Discrepancy (mg)",
         y = "subHR (95% CI)",
         title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) -> p
  .save_plot_pptx(p)
  p
}

plot_cox_linear <- function(time_var, status_var, extra_adj = NULL,
                            outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ dose_discrepancy + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- tryCatch(survival::coxph(fmla, data = d), error = function(e) NULL)
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- coef(fit)["dose_discrepancy"]
  V_beta <- vcov(fit)["dose_discrepancy", "dose_discrepancy"]

  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$dose_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "Dose Discrepancy (mg)",
         y = "HR (95% CI)",
         title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) -> p
  .save_plot_pptx(p)
  p
}
```

## 11.1 Anemia Grade 2

```{r}
#| label: jx-carbo-linsubhr-dosedisc-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_2", "cmp_status_anemia_2",
                  "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 11.2 Anemia Grade 3

```{r}
#| label: jx-carbo-linsubhr-dosedisc-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_3", "cmp_status_anemia_3",
                  "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 11.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-linsubhr-dosedisc-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_2", "cmp_status_throm_2",
                  "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 11.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-linsubhr-dosedisc-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_3", "cmp_status_throm_3",
                  "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 11.5 AKI Grade 2

```{r}
#| label: jx-carbo-linsubhr-dosedisc-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_2", "cmp_status_aki_2",
                  NULL, "AKI Grade 2 (Carboplatin)")
```

## 11.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-linsubhr-dosedisc-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                  NULL, "AKI (KDIGO) (Carboplatin)")
```

## 11.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-linsubhr-dosedisc-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                  NULL, "Composite Grade 2 AEs (Carboplatin)")
```

## 11.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-linsubhr-dosedisc-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                  NULL, "Composite Grade 3 AEs (Carboplatin)")
```

## 11.9 Overall Hospitalization

```{r}
#| label: jx-carbo-linsubhr-dosedisc-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_any_hosp", "cmp_status_any_hosp",
                  NULL, "Overall Hospitalization (Carboplatin)")
```

## 11.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-linsubhr-dosedisc-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_side_effect", "cmp_status_side_effect",
                  NULL, "Platinum-Related Hospitalization (Carboplatin)")
```

## 11.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-linsubhr-dosedisc-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear("time_to_death_90", "death_90",
                NULL, "90-Day Death (Cox PH) (Carboplatin)")
```

# 12 Linear subHR Curves — Hospitalization by Reason (Carboplatin)

## 13.1 Nausea/Vomiting/GI

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp1
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_1", "cmp_status_hosp_1",
                        NULL, "Nausea/Vomiting/GI (Carboplatin)")
```

## 13.2 Failure to Thrive/Fatigue/Dehydration

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_2", "cmp_status_hosp_2",
                        NULL, "Failure to Thrive/Fatigue/Dehydration (Carboplatin)")
```

## 13.3 AKI

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_3", "cmp_status_hosp_3",
                        NULL, "AKI (Carboplatin)")
```

## 13.4 Electrolyte Abnormalities

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp4
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_4", "cmp_status_hosp_4",
                        NULL, "Electrolyte Abnormalities (Carboplatin)")
```

## 13.5 Cytopenia

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp5
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_5", "cmp_status_hosp_5",
                        NULL, "Cytopenia (Carboplatin)")
```

## 13.6 Febrile Neutropenia

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp6
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_6", "cmp_status_hosp_6",
                        NULL, "Febrile Neutropenia (Carboplatin)")
```

## 13.7 Infection/Sepsis

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp7
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_7", "cmp_status_hosp_7",
                        NULL, "Infection/Sepsis (Carboplatin)")
```

## 13.8 Cancer Progression

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp8
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_8", "cmp_status_hosp_8",
                        NULL, "Cancer Progression (Carboplatin)")
```

## 13.9 Immune-related AE & Other

Composite competing-risk outcome combining hospitalisations coded as Immune-related AE (reason 9) and Other (reason 11). Event = 1 if either occurred within 90 days; time = earliest of the two.

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp-immune-other
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_immune_other",
                        "cmp_status_hosp_immune_other",
                        NULL, "Immune-related AE & Other (Carboplatin)")
```

## 13.10 Planned Surgery/Port

```{r}
#| label: jx-carbo-linsubhr-ratio-hosp10
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_10", "cmp_status_hosp_10",
                        NULL, "Planned Surgery/Port (Carboplatin)")
```

# 13 Scatter Plots — Dose Discrepancy vs eGFR (Carboplatin)

## 13.1 Dose Discrepancy vs CKD-EPI Cr-Cys (unindexed)

```{r}
#| label: jx-carbo-scatter-epi
#| fig-width: 6
#| fig-height: 4
ggplot(dat %>% filter(!is.na(dose_discrepancy)),
       aes(x = ckd_epi_gfr_cre_cys_unindex, y = dose_discrepancy)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
  labs(x = "CKD-EPI Cr-Cys eGFR (unindexed, mL/min)",
       y = "Dose Discrepancy (mg)",
       title = "Dose Discrepancy vs CKD-EPI Cr-Cys eGFR (Carboplatin)") +
  theme_minimal(base_size = 11)
```

## 13.2 Dose Discrepancy vs Cockcroft-Gault

```{r}
#| label: jx-carbo-scatter-cg
#| fig-width: 6
#| fig-height: 4
ggplot(dat %>% filter(!is.na(dose_discrepancy)),
       aes(x = cockcroft, y = dose_discrepancy)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
  labs(x = "Cockcroft-Gault eGFR (mL/min)",
       y = "Dose Discrepancy (mg)",
       title = "Dose Discrepancy vs Cockcroft-Gault eGFR (Carboplatin)") +
  theme_minimal(base_size = 11)
```


# 14 Adjusted CIF — Dose Discrepancy >= +25 mg (Carboplatin)

Standardized cumulative incidence functions for each competing-risk outcome, contrasting patients with `dose_discrepancy >= 25` (red) against those with `dose_discrepancy < 25` (blue). The Fine-Gray model is fit with the binary exposure plus the same adjuster set used in Section 7. Curves are *adjusted (standardized)* via g-computation: for every patient, predict CIF under exposure = 1 and under exposure = 0, then average the two CIF curves over the cohort. Y-axis is cumulative incidence, x-axis is days from baseline.

90-day death (Section 14.11) is modelled with Cox PH instead of Fine-Gray (no competing event), and the standardized cumulative-incidence-of-death curve is `1 − S(t|Xᵢ)` averaged across the cohort.

```{r}
#| label: jx-carbo-adjcif-helper
adj_cif <- function(time_var, status_var, extra_pre = NULL, label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  vars <- c("dose_discrep_ge25", base_adj, extra_pre)
  d <- dat %>%
    dplyr::select(all_of(c(time_var, status_var, vars))) %>%
    tidyr::drop_na()

  fmla <- as.formula(paste("~",
            paste(c("dose_discrep_ge25", base_adj, extra_pre), collapse = " + ")))
  X_full <- model.matrix(fmla, data = d)[, -1, drop = FALSE]

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- tryCatch(
    cmprsk::crr(ftime = time_num, fstatus = stat_num,
                cov1 = X_full, failcode = 1),
    error = function(e) NULL
  )
  if (is.null(fit)) return(.plot_failed(label))

  # subHR (95% CI) for the binary exposure, extracted from the same FG fit
  # dose_discrep_ge25 is the first column of cov1 (entered first in the formula)
  beta_e <- unname(fit$coef[1])
  se_e   <- sqrt(fit$var[1, 1])
  hr     <- exp(beta_e)
  lcl    <- exp(beta_e - 1.96 * se_e)
  ucl    <- exp(beta_e + 1.96 * se_e)
  pval   <- 2 * (1 - pnorm(abs(beta_e / se_e)))
  p_str  <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
  subtitle_str <- sprintf(
    "Discrep >= +25 vs <+25: subHR = %.2f (95%% CI %.2f-%.2f), p = %s",
    hr, lcl, ucl, p_str
  )

  X0 <- X_full; X0[, "dose_discrep_ge25"] <- 0
  X1 <- X_full; X1[, "dose_discrep_ge25"] <- 1

  pred0 <- predict(fit, X0)
  pred1 <- predict(fit, X1)

  times <- pred0[, 1]
  cif0  <- rowMeans(pred0[, -1, drop = FALSE])
  cif1  <- rowMeans(pred1[, -1, drop = FALSE])

  df <- bind_rows(
    tibble(time = times, cif = cif0, group = "Discrep < +25 mg"),
    tibble(time = times, cif = cif1, group = "Discrep >= +25 mg")
  )

  ymax <- max(df$cif, na.rm = TRUE)

  ggplot(df, aes(x = time, y = cif, color = group)) +
    geom_step(linewidth = 1) +
    scale_color_manual(values = c("Discrep < +25 mg"  = "#1F78B4",
                                  "Discrep >= +25 mg" = "#E31A1C")) +
    coord_cartesian(ylim = c(0, max(0.05, ymax * 1.05))) +
    labs(x = "Days from baseline",
         y = "Cumulative incidence",
         color = NULL,
         title = label,
         subtitle = subtitle_str) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "top",
          plot.subtitle = element_text(size = 10, color = "grey25")) -> p
  .save_plot_pptx(p)
  p
}

adj_death_curve <- function(time_var = "time_to_death_90",
                            status_var = "death_90", label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  vars <- c("dose_discrep_ge25", base_adj)
  d <- dat %>%
    dplyr::select(all_of(c(time_var, status_var, vars))) %>%
    tidyr::drop_na()

  rhs <- paste(c("dose_discrep_ge25", base_adj), collapse = " + ")
  fmla <- as.formula(sprintf("survival::Surv(%s, %s) ~ %s",
                             time_var, status_var, rhs))
  fit <- tryCatch(survival::coxph(fmla, data = d), error = function(e) NULL)
  if (is.null(fit)) return(.plot_failed(label))

  beta_e <- unname(coef(fit)["dose_discrep_ge25"])
  se_e   <- sqrt(vcov(fit)["dose_discrep_ge25", "dose_discrep_ge25"])
  hr     <- exp(beta_e)
  lcl    <- exp(beta_e - 1.96 * se_e)
  ucl    <- exp(beta_e + 1.96 * se_e)
  pval   <- 2 * (1 - pnorm(abs(beta_e / se_e)))
  p_str  <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
  subtitle_str <- sprintf(
    "Discrep >= +25 vs <+25: HR = %.2f (95%% CI %.2f-%.2f), p = %s   (Cox PH)",
    hr, lcl, ucl, p_str
  )

  d0 <- d; d0$dose_discrep_ge25 <- 0
  d1 <- d; d1$dose_discrep_ge25 <- 1

  sf0 <- survival::survfit(fit, newdata = d0)
  sf1 <- survival::survfit(fit, newdata = d1)

  s0 <- if (is.matrix(sf0$surv)) sf0$surv else as.matrix(sf0$surv)
  s1 <- if (is.matrix(sf1$surv)) sf1$surv else as.matrix(sf1$surv)

  cif0 <- 1 - rowMeans(s0)
  cif1 <- 1 - rowMeans(s1)

  df <- bind_rows(
    tibble(time = sf0$time, cif = cif0, group = "Discrep < +25 mg"),
    tibble(time = sf1$time, cif = cif1, group = "Discrep >= +25 mg")
  )

  ymax <- max(df$cif, na.rm = TRUE)

  ggplot(df, aes(x = time, y = cif, color = group)) +
    geom_step(linewidth = 1) +
    scale_color_manual(values = c("Discrep < +25 mg"  = "#1F78B4",
                                  "Discrep >= +25 mg" = "#E31A1C")) +
    coord_cartesian(ylim = c(0, max(0.05, ymax * 1.05))) +
    labs(x = "Days from baseline",
         y = "Cumulative incidence (1 - S)",
         color = NULL,
         title = label,
         subtitle = subtitle_str) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "top",
          plot.subtitle = element_text(size = 10, color = "grey25")) -> p
  .save_plot_pptx(p)
  p
}
```

## 14.1 Anemia Grade 2

```{r}
#| label: jx-carbo-adjcif-anemia2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_anemia_2", "cmp_status_anemia_2",
        "pre_HGB_45days", "Anemia Grade 2")
```

## 14.2 Anemia Grade 3

```{r}
#| label: jx-carbo-adjcif-anemia3
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_anemia_3", "cmp_status_anemia_3",
        "pre_HGB_45days", "Anemia Grade 3")
```

## 14.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-adjcif-throm2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_throm_2", "cmp_status_throm_2",
        "pre_PLT_45days", "Thrombocytopenia Grade 2")
```

## 14.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-adjcif-throm3
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_throm_3", "cmp_status_throm_3",
        "pre_PLT_45days", "Thrombocytopenia Grade 3")
```

## 14.5 AKI Grade 2

```{r}
#| label: jx-carbo-adjcif-aki2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_aki_2", "cmp_status_aki_2",
        NULL, "AKI Grade 2")
```

## 14.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-adjcif-akikdigo
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
        NULL, "AKI (KDIGO)")
```

## 14.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-adjcif-grade2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
        NULL, "Composite Grade 2 AEs")
```

## 14.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-adjcif-grade3
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
        NULL, "Composite Grade 3 AEs")
```

## 14.9 Overall Hospitalization

```{r}
#| label: jx-carbo-adjcif-anyhosp
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_any_hosp", "cmp_status_any_hosp",
        NULL, "Overall Hospitalization")
```

## 14.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-adjcif-sideeffect
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_side_effect", "cmp_status_side_effect",
        NULL, "Platinum-Related Hospitalization")
```

## 14.11 90-Day Death (Cox PH)

```{r}
#| label: jx-carbo-adjcif-death
#| fig-width: 7
#| fig-height: 4
adj_death_curve("time_to_death_90", "death_90", "90-Day Death")
```

# 15 Paper

```{r}
#| label: jx-carbo-paper-stats
#| include: false
n_excess  <- sum(dat$dose_discrep_ge25 == 1, na.rm = TRUE)
n_with_dx <- sum(!is.na(dat$dose_discrepancy))
pct_excess <- round(n_excess / n_with_dx * 100, 1)
```

A total of `r n_excess` (`r pct_excess`%) patients received an excess dose of carboplatin, defined as ≥ 25 mg higher than the dose that would have been predicted using the CKD-EPI eGFR~CR-CYS~ equation adjusted for actual BSA.

(Denominator: `r n_with_dx` carboplatin patients with a computable predicted dose.)

# 16 Diagnostic — Local/Early Stage Patients (Record IDs)

The carboplatin cohort contains a small number of patients with `tumor_stage` = **Local/Early**. Their record IDs are listed below — useful for QA / chart review.

```{r}
#| label: jx-carbo-local-early-ids
local_early <- dat %>%
  dplyr::filter(as.character(tumor_stage) %in% c("Local/Early", "1")) %>%
  dplyr::select(record_id, EMPI, tumor_stage, cancer_type_cat_7, age, sex) %>%
  dplyr::arrange(record_id)

knitr::kable(
  local_early,
  align = c("r","r","l","l","r","l"),
  caption = sprintf("Carboplatin cohort patients with tumor_stage = Local/Early (N = %d).",
                    nrow(local_early))
)
```

# 17 Downloadable PowerPoint Plots

Every figure on this page is also saved as an editable **PowerPoint slide** (vector graphics — text and shapes remain editable in PowerPoint). Click any link below to download the .pptx for that figure.

```{r}
#| label: jx-carbo-pptx-index
#| results: asis
pptx_files <- list.files(pptx_dir, pattern = "\\.pptx$", full.names = FALSE)
if (length(pptx_files) == 0) {
  cat("*No PowerPoint files were produced during this render.*\n")
} else {
  for (f in sort(pptx_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("- [📥 %s](../plots/carbo/%s)\n", label, f))
  }
}
```
