---
title: "Sherley Project — Grant Figures"
author: "Tianqi Ouyang"
date: "2026-09-08"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

Grant-figure versions of the Carboplatin Cohort analyses, re-expressed on the
**eGFR difference** scale.

$$
\text{eGFR difference (\%)} \;=\; \frac{\text{eGFR}_{\text{CR-CYS}} - \text{CrCl}_{\text{CG}}}{\text{CrCl}_{\text{CG}}} \times 100
$$

Both terms in the numerator are in **mL/min**: the CKD-EPI creatinine–cystatin C
eGFR is the version **adjusted for actual body surface area**
(`ckd_epi_gfr_cre_cys_unindex`, mL/min — *not* the 1.73 m²-indexed
`ckd_epi_gfr_cre_cys`), matching the units of Cockcroft-Gault creatinine
clearance. The result is expressed as a **percentage**: `0 %` means the two
estimators agree, `+20 %` means CKD-EPI Cr-Cys is 20 % higher than
Cockcroft-Gault, `−20 %` means 20 % lower.

::: {.callout-note}
## Relationship to the eGFR ratio used on the Carboplatin page
Because `egfr_difference = 100 × ((eGFR − CG) / CG) = 100 × (egfr_ratio − 1)`,
this is a pure re-centring and rescaling of the eGFR ratio: the reference point
moves from 1 to 0 %. The underlying Fine-Gray fits are therefore the same models
as §9 of the Carboplatin Cohort page — identical p-values. The reported subHRs
differ only because this page reports them **per 10 % decrease** in eGFR
difference, whereas §9 reports per 0.1-unit *increase* in the ratio; the two are
reciprocals of each other.
:::

```{r}
#| label: setup-jx-grant
# Force UTF-8 locale so captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)
library(officer)
library(rvg)

# Output directory for downloadable PowerPoint plots (../plots/grant/<name>.pptx).
pptx_dir <- normalizePath("docs/plots/grant", winslash = "/", mustWork = FALSE)
dir.create(pptx_dir, recursive = TRUE, showWarnings = FALSE)

# Save the given ggplot as an editable PowerPoint slide via rvg::dml, named by
# the calling chunk's label. Mirrors the helper in sherley_carbo.qmd; the
# post-render script scripts/inject_pptx_links.py then injects a per-plot
# download link beneath each figure in the rendered HTML.
.save_plot_pptx <- function(p, name = NULL) {
  if (is.null(p) || !inherits(p, "ggplot")) return(invisible(NULL))
  if (is.null(name)) {
    name <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  }
  if (is.null(name)) return(invisible(NULL))
  safe <- gsub("[^A-Za-z0-9]+", "_", name)
  out  <- file.path(pptx_dir, paste0(safe, ".pptx"))
  ok <- tryCatch({
    pp <- officer::read_pptx()
    pp <- officer::add_slide(pp, layout = "Title and Content", master = "Office Theme")
    pp <- officer::ph_with(
      pp,
      value = rvg::dml(ggobj = p),
      location = officer::ph_location_type(type = "body")
    )
    print(pp, target = out)
    TRUE
  }, error = function(e) FALSE)
  invisible(if (ok) paste0("../plots/grant/", safe, ".pptx") else NULL)
}

# Format the exposure-effect subtitle: subHR (or HR) per `scale` units with
# 95% Wald CI and p-value, extracted from the Fine-Gray / Cox PH fit.
.hr_subtitle <- function(beta, V_beta, scale = 1,
                         hr_type = "subHR",
                         unit_label = "per 1-unit increase") {
  se   <- sqrt(V_beta)
  hr   <- exp(beta * scale)
  b1   <- exp((beta - 1.96 * se) * scale)
  b2   <- exp((beta + 1.96 * se) * scale)
  # A negative `scale` (reporting per unit DECREASE) reverses the bound order,
  # so sort rather than assuming b1 <= b2.
  lcl  <- min(b1, b2)
  ucl  <- max(b1, b2)
  pval <- 2 * (1 - pnorm(abs(beta / se)))
  p_str <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
  sprintf("%s = %.2f (95%% CI %.2f-%.2f), p = %s   (%s)",
          hr_type, hr, lcl, ucl, p_str, unit_label)
}

# Placeholder for outcomes whose design matrix is singular on this sub-cohort.
.plot_failed <- function(label = "Model could not be fit") {
  p <- ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = paste0(label, "\n(singular design — cohort too small)"),
             size = 3.5) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) +
    theme_void()
  .save_plot_pptx(p)
  p
}

# Load whole-cohort data, then keep only carboplatin patients
dat <- readRDS("sherley_final_master.rds") %>%
  filter(platin_group == "Carboplatin")

dat <- dat %>%
  mutate(
    # BSA-adjusted CKD-EPI Cr-Cys (mL/min) vs Cockcroft-Gault CrCl (mL/min).
    # Relative difference expressed as a PERCENT; 0 % = the two estimators agree.
    egfr_difference = 100 * (ckd_epi_gfr_cre_cys_unindex - cockcroft) / cockcroft
  )

cat("Carboplatin cohort N =", nrow(dat), "\n")
cat("eGFR difference available for N =", sum(!is.na(dat$egfr_difference)), "\n")
```

# 2 Carboplatin Dose Administered

Actual carboplatin dose administered (REDCap field `carbo_dose_redcap`, mg) across
the 121-patient carboplatin cohort. All 121 have a thoracic primary and every
patient has a recorded dose, so the denominator is the full cohort.

```{r}
#| label: jx-grant-carbo-dose-summary
dose_vals <- dat$carbo_dose_redcap
dose_vals <- dose_vals[!is.na(dose_vals)]

tibble::tibble(
  Statistic = c("N with a recorded dose", "Mean (SD)", "Median (IQR)",
                "Range (min – max)"),
  Value = c(
    as.character(length(dose_vals)),
    sprintf("%.1f (%.1f) mg", mean(dose_vals), sd(dose_vals)),
    sprintf("%.1f (%.1f, %.1f) mg", median(dose_vals),
            quantile(dose_vals, 0.25), quantile(dose_vals, 0.75)),
    sprintf("%.1f – %.1f mg", min(dose_vals), max(dose_vals))
  )
) %>%
  knitr::kable(align = c("l", "r"),
               caption = "Actual carboplatin dose administered (mg), carboplatin cohort.")
```

# 3 eGFR Difference Distribution (Carboplatin)

Mirrors §4 of the Carboplatin Cohort page, re-expressed as a percentage. Bins are
10 % wide with an axis tick at every bin edge. The red dashed line marks
**−10 %** — the randomization cutoff.

```{r}
#| label: jx-grant-egfr-diff-hist
#| fig-width: 9
#| fig-height: 5
diff_hist <- dat %>% filter(!is.na(egfr_difference))

ggplot(diff_hist, aes(x = egfr_difference)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count)) * 100),
                 binwidth = 10, boundary = 0,
                 fill = "steelblue", color = "black", alpha = 0.7) +
  geom_vline(xintercept = -10, linetype = "dashed", color = "red",
             linewidth = 1.1) +
  labs(title = "Distribution of eGFR Difference (Carboplatin)",
       subtitle = expression(paste("eGFR difference (%) = (eGFR"[CR-CYS],
                                   " − CrCl"[CG], ") / CrCl"[CG], " × 100;  red line = −10 % cutoff")),
       x = "eGFR difference (%)",
       y = "Percent of Patients (%)") +
  scale_x_continuous(breaks = seq(-100, 200, 10)) +
  theme_minimal(base_size = 14) +
  theme(plot.subtitle = element_text(size = 11, color = "grey25")) -> p
.save_plot_pptx(p)
p
```

```{r}
#| label: jx-grant-egfr-diff-summary
q <- quantile(diff_hist$egfr_difference, c(0.025, 0.25, 0.5, 0.75, 0.975),
              na.rm = TRUE)
tibble::tibble(
  Statistic = c("N", "Median", "IQR (p25, p75)", "2.5th pct", "97.5th pct",
                "% with eGFR Cr-Cys below CG (difference < 0 %)",
                "% at or below the −10 % randomization cutoff"),
  Value = c(
    as.character(nrow(diff_hist)),
    sprintf("%.1f%%", q[["50%"]]),
    sprintf("%.1f%%, %.1f%%", q[["25%"]], q[["75%"]]),
    sprintf("%.1f%%", q[["2.5%"]]),
    sprintf("%.1f%%", q[["97.5%"]]),
    sprintf("%.1f%%", 100 * mean(diff_hist$egfr_difference < 0)),
    sprintf("%.1f%% (n = %d)",
            100 * mean(diff_hist$egfr_difference <= -10),
            sum(diff_hist$egfr_difference <= -10))
  )
) %>%
  knitr::kable(align = c("l", "r"),
               caption = "eGFR difference (%) — distribution summary (carboplatin cohort).")
```

# 4 Predicted Dosing in the eGFR Difference ≤ −10 % Subgroup

The patients who would meet the **−10 % randomization cutoff** — those whose
BSA-adjusted CKD-EPI Cr-Cys eGFR sits at least 10 % below their Cockcroft-Gault
creatinine clearance. For this subgroup the table contrasts the carboplatin dose
the Calvert formula would have produced from each kidney-function estimator
against the dose actually given.

Predicted doses use Calvert at the patient's own target AUC:
`dose = AUC × (min(eGFR, 125) + 25)`. **Both arms cap the filtration estimate at
125 mL/min**, so the comparison is symmetric — `carbo_dose_cre_cys` from the data
pipeline already applies the cap (verified: it reproduces the capped formula
exactly, and differs from the uncapped one by up to 53 mg), and the
Cockcroft-Gault arm applies the same `min(CG, 125)`.

The cap binds more often on the Cockcroft-Gault side in this subgroup — 11 of 39
patients exceed 125 mL/min by CG versus 3 of 39 by CKD-EPI Cr-Cys — which is
expected, since the subgroup is selected for CG running high relative to Cr-Cys.
The cap is therefore doing real work here: without it the Cr-Cys − CG dose gap
would widen from **−75.1 (41.1) mg** to **−113.2 (87.4) mg**.

```{r}
#| label: jx-grant-sub10-dose-table
sub10 <- dat %>%
  filter(!is.na(egfr_difference), egfr_difference <= -10) %>%
  mutate(carbo_dose_cg = carbo_AUC * (pmin(cockcroft, 125) + 25))

# mean (SD) and median (IQR) for one column, formatted to 1 dp.
.msd <- function(x) {
  x <- x[!is.na(x)]
  c(sprintf("%.1f (%.1f)", mean(x), stats::sd(x)),
    sprintf("%.1f (%.1f, %.1f)", stats::median(x),
            stats::quantile(x, .25), stats::quantile(x, .75)))
}

.rows <- list(
  list("Predicted dose — CKD-EPI Cr-Cys (mg)",  sub10$carbo_dose_cre_cys),
  list("Predicted dose — Cockcroft-Gault (mg)", sub10$carbo_dose_cg),
  list("Actual dose administered (mg)",         sub10$carbo_dose_redcap),
  list("Difference — Cr-Cys − Cockcroft-Gault (mg)",
       sub10$carbo_dose_cre_cys - sub10$carbo_dose_cg),
  list("Difference — Cr-Cys − actual dose (mg)",
       sub10$carbo_dose_cre_cys - sub10$carbo_dose_redcap)
)

purrr::map_dfr(.rows, function(r) {
  v <- .msd(r[[2]])
  tibble::tibble(Measure = r[[1]], `Mean (SD)` = v[1], `Median (IQR)` = v[2])
}) %>%
  knitr::kable(
    align = c("l", "r", "r"),
    caption = sprintf(
      "Carboplatin dosing among patients with eGFR difference ≤ −10 %% (n = %d of %d carboplatin patients, %.1f %%). Negative differences mean the CKD-EPI Cr-Cys equation would have dosed lower.",
      nrow(sub10), nrow(dat), 100 * nrow(sub10) / nrow(dat)))
```

# 5 Linear subHR Curves — eGFR Difference (Carboplatin)

Mirrors §9.1–9.10 of the Carboplatin Cohort page, with the exposure re-expressed
as the eGFR difference in **percent** (ticks every 10 %). Each curve is the
adjusted Fine-Gray subdistribution hazard ratio as a smooth linear function of
the eGFR difference, plotted relative to the cohort median (dotted vertical
line). The dashed horizontal line marks subHR = 1. **Reported subHRs are per
10 % _decrease_ in eGFR difference**, so a subHR above 1 means a larger
CKD-EPI-Cr-Cys shortfall relative to Cockcroft-Gault carries higher risk. Models
adjust for age, sex, ECOG score, ICI use and
Cockcroft-Gault CrCl, plus baseline haemoglobin (anemia), baseline platelets
(thrombocytopenia) or both (composite cytopenia outcomes).

```{r}
#| label: jx-grant-linsubhr-diff-helper
plot_subhr_linear_diff <- function(time_var, status_var, extra_adj = NULL,
                                   outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("egfr_difference", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_difference = d$egfr_difference, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- tryCatch(
    cmprsk::crr(ftime = time_num, fstatus = stat_num,
                cov1 = X, failcode = 1),
    error = function(e) NULL
  )
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  # egfr_difference is in percentage points, so beta is per 1 pp. Report per
  # 10 % DECREASE => scale = -10 (negative direction handled in .hr_subtitle).
  subtitle_str <- .hr_subtitle(beta, V_beta, scale = -10,
                               hr_type = "subHR",
                               unit_label = "per 10% decrease")

  ref_x  <- median(d$egfr_difference, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_difference, 0.025, na.rm = TRUE),
                quantile(d$egfr_difference, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "eGFR difference (%)",
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    scale_x_continuous(breaks = seq(-100, 100, 10)) +
    coord_cartesian(xlim = c(-35, 45), ylim = c(0, 4)) +
    theme_minimal(base_size = 14) +
    theme(plot.subtitle = element_text(size = 10, color = "grey25")) -> p
  .save_plot_pptx(p)
  p
}
```

## 5.1 Anemia Grade 2

```{r}
#| label: jx-grant-linsubhr-diff-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_anemia_2", "cmp_status_anemia_2",
                       "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 5.2 Anemia Grade 3

```{r}
#| label: jx-grant-linsubhr-diff-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_anemia_3", "cmp_status_anemia_3",
                       "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-grant-linsubhr-diff-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_throm_2", "cmp_status_throm_2",
                       "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-grant-linsubhr-diff-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_throm_3", "cmp_status_throm_3",
                       "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 5.5 AKI Grade 2

```{r}
#| label: jx-grant-linsubhr-diff-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_aki_2", "cmp_status_aki_2",
                       NULL, "AKI Grade 2 (Carboplatin)")
```

## 5.6 AKI (KDIGO)

```{r}
#| label: jx-grant-linsubhr-diff-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                       NULL, "AKI (KDIGO) (Carboplatin)")
```

## 5.7 Composite Grade 2 AEs

```{r}
#| label: jx-grant-linsubhr-diff-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                       c("pre_HGB_45days", "pre_PLT_45days"),
                       "Composite Grade 2 AEs (Carboplatin)")
```

## 5.8 Composite Grade 3 AEs

```{r}
#| label: jx-grant-linsubhr-diff-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                       c("pre_HGB_45days", "pre_PLT_45days"),
                       "Composite Grade 3 AEs (Carboplatin)")
```

## 5.9 Overall Hospitalization

```{r}
#| label: jx-grant-linsubhr-diff-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_any_hosp", "cmp_status_any_hosp",
                       NULL, "Overall Hospitalization (Carboplatin)")
```

## 5.10 Platinum-Related Hospitalization

```{r}
#| label: jx-grant-linsubhr-diff-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_side_effect", "cmp_status_side_effect",
                       NULL, "Platinum-Related Hospitalization (Carboplatin)")
```

# 6 Downloadable PowerPoint Plots

Every figure on this page is also saved as an editable **PowerPoint slide**
(vector graphics — text and shapes remain editable in PowerPoint). Click any
link below to download the .pptx for that figure.

```{r}
#| label: jx-grant-pptx-index
#| results: asis
pptx_files <- list.files(pptx_dir, pattern = "\\.pptx$", full.names = FALSE)
if (length(pptx_files) == 0) {
  cat("*No PowerPoint files were produced during this render.*\n")
} else {
  for (f in sort(pptx_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("- [📥 %s](../plots/grant/%s)\n", label, f))
  }
}
```
