---
title: "Sherley Project — Grant Figures"
author: "Tianqi Ouyang"
date: "2026-09-08"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

Grant-figure versions of the Carboplatin Cohort analyses, re-expressed on the
**eGFR difference** scale.

$$
\text{eGFR difference} \;=\; \frac{\text{eGFR}_{\text{CR-CYS}} - \text{CrCl}_{\text{CG}}}{\text{CrCl}_{\text{CG}}}
$$

Both terms in the numerator are in **mL/min**: the CKD-EPI creatinine–cystatin C
eGFR is the version **adjusted for actual body surface area**
(`ckd_epi_gfr_cre_cys_unindex`, mL/min — *not* the 1.73 m²-indexed
`ckd_epi_gfr_cre_cys`), matching the units of Cockcroft-Gault creatinine
clearance. The resulting difference is a **unitless relative difference**:
`0` means the two estimators agree, `+0.20` means CKD-EPI Cr-Cys is 20 % higher
than Cockcroft-Gault, `-0.20` means 20 % lower.

::: {.callout-note}
## Relationship to the eGFR ratio used on the Carboplatin page
Because `egfr_difference = (eGFR − CG) / CG = egfr_ratio − 1`, this is a pure
re-centring of the eGFR ratio: the reference point moves from 1 to 0. The
Fine-Gray coefficients, standard errors and p-values are therefore **identical**
to the corresponding figures in §9 of the Carboplatin Cohort page — only the
x-axis scale differs.
:::

```{r}
#| label: setup-jx-grant
# Force UTF-8 locale so captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)
library(officer)
library(rvg)

# Output directory for downloadable PowerPoint plots (../plots/grant/<name>.pptx).
pptx_dir <- normalizePath("docs/plots/grant", winslash = "/", mustWork = FALSE)
dir.create(pptx_dir, recursive = TRUE, showWarnings = FALSE)

# Save the given ggplot as an editable PowerPoint slide via rvg::dml, named by
# the calling chunk's label. Mirrors the helper in sherley_carbo.qmd; the
# post-render script scripts/inject_pptx_links.py then injects a per-plot
# download link beneath each figure in the rendered HTML.
.save_plot_pptx <- function(p, name = NULL) {
  if (is.null(p) || !inherits(p, "ggplot")) return(invisible(NULL))
  if (is.null(name)) {
    name <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  }
  if (is.null(name)) return(invisible(NULL))
  safe <- gsub("[^A-Za-z0-9]+", "_", name)
  out  <- file.path(pptx_dir, paste0(safe, ".pptx"))
  ok <- tryCatch({
    pp <- officer::read_pptx()
    pp <- officer::add_slide(pp, layout = "Title and Content", master = "Office Theme")
    pp <- officer::ph_with(
      pp,
      value = rvg::dml(ggobj = p),
      location = officer::ph_location_type(type = "body")
    )
    print(pp, target = out)
    TRUE
  }, error = function(e) FALSE)
  invisible(if (ok) paste0("../plots/grant/", safe, ".pptx") else NULL)
}

# Format the exposure-effect subtitle: subHR (or HR) per `scale` units with
# 95% Wald CI and p-value, extracted from the Fine-Gray / Cox PH fit.
.hr_subtitle <- function(beta, V_beta, scale = 1,
                         hr_type = "subHR",
                         unit_label = "per 1-unit increase") {
  se   <- sqrt(V_beta)
  hr   <- exp(beta * scale)
  lcl  <- exp((beta - 1.96 * se) * scale)
  ucl  <- exp((beta + 1.96 * se) * scale)
  pval <- 2 * (1 - pnorm(abs(beta / se)))
  p_str <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
  sprintf("%s = %.2f (95%% CI %.2f-%.2f), p = %s   (%s)",
          hr_type, hr, lcl, ucl, p_str, unit_label)
}

# Placeholder for outcomes whose design matrix is singular on this sub-cohort.
.plot_failed <- function(label = "Model could not be fit") {
  p <- ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = paste0(label, "\n(singular design — cohort too small)"),
             size = 3.5) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) +
    theme_void()
  .save_plot_pptx(p)
  p
}

# Load whole-cohort data, then keep only carboplatin patients
dat <- readRDS("sherley_final_master.rds") %>%
  filter(platin_group == "Carboplatin")

dat <- dat %>%
  mutate(
    # BSA-adjusted CKD-EPI Cr-Cys (mL/min) vs Cockcroft-Gault CrCl (mL/min).
    # Relative difference — unitless; 0 = the two estimators agree.
    egfr_difference = (ckd_epi_gfr_cre_cys_unindex - cockcroft) / cockcroft
  )

cat("Carboplatin cohort N =", nrow(dat), "\n")
cat("eGFR difference available for N =", sum(!is.na(dat$egfr_difference)), "\n")
```

# 2 eGFR Difference Distribution (Carboplatin)

Mirrors §4 of the Carboplatin Cohort page, re-expressed on the eGFR difference
scale. The red dashed line at **0** marks perfect agreement between the
BSA-adjusted CKD-EPI Cr-Cys eGFR and Cockcroft-Gault creatinine clearance.

```{r}
#| label: jx-grant-egfr-diff-hist
#| fig-width: 8
#| fig-height: 5
diff_hist <- dat %>% filter(!is.na(egfr_difference))

ggplot(diff_hist, aes(x = egfr_difference)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count)) * 100),
                 binwidth = 0.1, boundary = 0,
                 fill = "steelblue", color = "black", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  labs(title = "Distribution of eGFR Difference (Carboplatin)",
       subtitle = expression(paste("eGFR difference = (BSA-adjusted eGFR"[CR-CYS],
                                   " − CrCl"[CG], ") / CrCl"[CG])),
       x = expression(paste("eGFR difference  =  (eGFR"[CR-CYS],
                            " − CrCl"[CG], ") / CrCl"[CG], "   (mL/min basis)")),
       y = "Percent of Patients (%)") +
  scale_x_continuous(breaks = seq(-1, 2, 0.2)) +
  theme_minimal(base_size = 14) +
  theme(plot.subtitle = element_text(size = 12, color = "grey25")) -> p
.save_plot_pptx(p)
p
```

```{r}
#| label: jx-grant-egfr-diff-summary
q <- quantile(diff_hist$egfr_difference, c(0.025, 0.25, 0.5, 0.75, 0.975),
              na.rm = TRUE)
tibble::tibble(
  Statistic = c("N", "Median", "IQR (p25, p75)", "2.5th pct", "97.5th pct",
                "% with eGFR Cr-Cys below CG (difference < 0)"),
  Value = c(
    as.character(nrow(diff_hist)),
    sprintf("%.3f", q[["50%"]]),
    sprintf("%.3f, %.3f", q[["25%"]], q[["75%"]]),
    sprintf("%.3f", q[["2.5%"]]),
    sprintf("%.3f", q[["97.5%"]]),
    sprintf("%.1f%%", 100 * mean(diff_hist$egfr_difference < 0))
  )
) %>%
  knitr::kable(align = c("l", "r"),
               caption = "eGFR difference — distribution summary (carboplatin cohort).")
```

# 3 Linear subHR Curves — eGFR Difference (Carboplatin)

Mirrors §9.1–9.10 of the Carboplatin Cohort page, with the exposure re-expressed
as the eGFR difference. Each curve is the adjusted Fine-Gray subdistribution
hazard ratio as a smooth linear function of the eGFR difference, plotted
relative to the cohort median (dotted vertical line). The dashed horizontal line
marks subHR = 1. Models adjust for age, sex, ECOG score, ICI use and
Cockcroft-Gault CrCl, plus baseline haemoglobin (anemia), baseline platelets
(thrombocytopenia) or both (composite cytopenia outcomes).

```{r}
#| label: jx-grant-linsubhr-diff-helper
plot_subhr_linear_diff <- function(time_var, status_var, extra_adj = NULL,
                                   outcome_label) {
  base_adj <- c("age", "sex", "ecog_score", "ici", "cockcroft")
  keep <- c("egfr_difference", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_difference = d$egfr_difference, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- tryCatch(
    cmprsk::crr(ftime = time_num, fstatus = stat_num,
                cov1 = X, failcode = 1),
    error = function(e) NULL
  )
  if (is.null(fit)) return(.plot_failed(outcome_label))

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  subtitle_str <- .hr_subtitle(beta, V_beta, scale = 0.1,
                               hr_type = "subHR",
                               unit_label = "per 0.1-unit increase in eGFR difference")

  ref_x  <- median(d$egfr_difference, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_difference, 0.025, na.rm = TRUE),
                quantile(d$egfr_difference, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = expression(paste("eGFR difference  =  (eGFR"[CR-CYS],
                              " − CrCl"[CG], ") / CrCl"[CG])),
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(xlim = c(-0.35, 0.45), ylim = c(0, 4)) +
    theme_minimal(base_size = 14) +
    theme(plot.subtitle = element_text(size = 12, color = "grey25")) -> p
  .save_plot_pptx(p)
  p
}
```

## 3.1 Anemia Grade 2

```{r}
#| label: jx-grant-linsubhr-diff-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_anemia_2", "cmp_status_anemia_2",
                       "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 3.2 Anemia Grade 3

```{r}
#| label: jx-grant-linsubhr-diff-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_anemia_3", "cmp_status_anemia_3",
                       "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 3.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-grant-linsubhr-diff-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_throm_2", "cmp_status_throm_2",
                       "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 3.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-grant-linsubhr-diff-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_throm_3", "cmp_status_throm_3",
                       "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 3.5 AKI Grade 2

```{r}
#| label: jx-grant-linsubhr-diff-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_aki_2", "cmp_status_aki_2",
                       NULL, "AKI Grade 2 (Carboplatin)")
```

## 3.6 AKI (KDIGO)

```{r}
#| label: jx-grant-linsubhr-diff-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                       NULL, "AKI (KDIGO) (Carboplatin)")
```

## 3.7 Composite Grade 2 AEs

```{r}
#| label: jx-grant-linsubhr-diff-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                       c("pre_HGB_45days", "pre_PLT_45days"),
                       "Composite Grade 2 AEs (Carboplatin)")
```

## 3.8 Composite Grade 3 AEs

```{r}
#| label: jx-grant-linsubhr-diff-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                       c("pre_HGB_45days", "pre_PLT_45days"),
                       "Composite Grade 3 AEs (Carboplatin)")
```

## 3.9 Overall Hospitalization

```{r}
#| label: jx-grant-linsubhr-diff-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_any_hosp", "cmp_status_any_hosp",
                       NULL, "Overall Hospitalization (Carboplatin)")
```

## 3.10 Platinum-Related Hospitalization

```{r}
#| label: jx-grant-linsubhr-diff-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_diff("cmp_time_side_effect", "cmp_status_side_effect",
                       NULL, "Platinum-Related Hospitalization (Carboplatin)")
```

# 4 Downloadable PowerPoint Plots

Every figure on this page is also saved as an editable **PowerPoint slide**
(vector graphics — text and shapes remain editable in PowerPoint). Click any
link below to download the .pptx for that figure.

```{r}
#| label: jx-grant-pptx-index
#| results: asis
pptx_files <- list.files(pptx_dir, pattern = "\\.pptx$", full.names = FALSE)
if (length(pptx_files) == 0) {
  cat("*No PowerPoint files were produced during this render.*\n")
} else {
  for (f in sort(pptx_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("- [📥 %s](../plots/grant/%s)\n", label, f))
  }
}
```
